### 2018-05-03 msc_diploma_cubesat_galgoczi.tex
added

\documentclass[12pt, a4paper,titlepage]{article}
\usepackage{ae}
\usepackage{lmodern}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{graphicx}
%\usepackage[margin=2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

%\usepackage{showkeys}
\usepackage{setspace}
\frenchspacing
\linespread{1.3}
\usepackage{indentfirst}
\usepackage[utf8]{inputenc}
\usepackage{float}

\usepackage{wrapfig}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage[calcwidth]{titlesec}
\usepackage{calc}

\usepackage{geometry}
%kotesre
\geometry{left=2.5cm,right=1.5cm,top=2.0cm,bottom=2.0cm}
%standard
%\geometry{left=2.0cm,right=2.0cm,top=2.0cm,bottom=2.0cm}

\newcommand*{\Resize}[2]{\resizebox{#1}{!}{$#2$}}%

\usepackage[pdftex]{hyperref}
	\hypersetup{colorlinks=true,
		pdfstartview=FitV,
		linkcolor=black,
		unicode=true,
		citecolor=black,
		urlcolor=black
		pdfauthor={Galgóczi Gábor, galgoczi.gabor@wigner.mta.hu},
		pdfsubject={TDK dolgozat},
		pdftitle={}
	}

	%\usepackage{biblatex}

%\usepackage[dvips]{graphicx}
%\usepackage{ucs}
%\usepackage[latin2]{inputenc}
%\usepackage{t1enc}
%\def\magyarOptions{defaults=prettiest}
%\usepackage[magyar]{babel}
%\usepackage{fontenc}
%\usepackage{graphicx}
%\usepackage{float}
%\usepackage{textcomp}
%\usepackage{array}
%\usepackage{tabularx}
%\usepackage{booktabs}
%\usepackage{color}
%\usepackage{ae}
%\usepackage{lmodern}
%\usepackage[margin=2 cm]{geometry}
%\usepackage{wrapfig}
%\usepackage{subfig}
%\usepackage{multirow}

\newcommand{\red}[1]{\textbf{\textcolor{red}{#1}}}
\newcommand{\pink}[1]{\textbf{\textcolor{magenta}{#1}}}
\newcommand{\blue}[1]{\textbf{\textcolor{blue}{#1}}}
\newcommand{\green}[1]{\textbf{\textcolor{green}{#1}}}
\usepackage[none]{hyphenat}
\sloppy
\titleformat{\section}{\large \bf }{\thesection.}{.5 em}{}[\vspace{-0.8 em}\rule{\titlewidth}{1pt}]

\begin{document}

\begin{titlepage}

\begin{center}
\ \\

\vspace{1 cm}
\begin{large}\textbf{Detailed feasibility study of a gamma ray detector system for nanosatellites using GEANT4 simulations}\end{large}\\
\vspace{1 cm}
%\begin{larger}\textbf{BSc szakdolgozat}\\ \end{larger}
%\vspace{0.5 cm}
\textit{\textbf{Galgóczi Gábor$^{*}$, Fizikus MSc szak, 2. évfolyam}}\\
Eötvös Loránd Tudományegyetem, Természettudományi Kar\\
WIGNER Fizikai Kutatóközpont - MTA\\
\vspace{1.5cm}
\begin{figure}[H]
\centering
\begin{tabular}{ >{\centering\arraybackslash}m{2in}  >{\centering\arraybackslash}m{2.5in}  }

\includegraphics[width=53.0mm]{images/regard.jpg}
\end{tabular}
\end{figure}

\begin{figure}[H]
\centering
\begin{tabular}{ >{\centering\arraybackslash}m{2in}  >{\centering\arraybackslash}m{2.5in}  }

\includegraphics[width=45.0mm]{images/elte.png} \parbox{0pt}{\rule{0pt}{2ex+\baselineskip}} &
\hspace{0.2 cm}
\includegraphics[width=40.0mm]{images/wigner.png}
\end{tabular}
\end{figure}

%\begin{figure}
%\centering
%\begin{subfigure}{5\textwidth}
 % \centering
  %\includegraphics[width=4\linewidth]{bme_logo_kicsi.jpg}
%\end{subfigure}%
%\begin{subfigure}{5\textwidth}
 % \centering
  %\includegraphics[width=4\linewidth]{image.jpg}
%\end{subfigure}
%\end{figure}

\vspace{0.1 cm}
\end{center}

\begin{center}
\begin{tabular}{ll}
\centerline{ Témavezetők: } \\
\centerline{ Conseil Européen pour la Recherche Nucléaire (CERN)}
\end{tabular}
\end{center}
\begin{center}

\vspace{2.5 cm}
\large \textbf {2016}\\
\end{center}
\end{titlepage}
%\doublespacing
\tableofcontents
%\singlespacing
\pagenumbering{roman}

\pagebreak
\pagenumbering{arabic}
\setcounter{page}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

High energy astrophysics

\subsection{Aim of the simulation}

The main aim of the paper, therefore this thesis is to optimize the scintillators of the CubeSats (miniaturized satellites) in the Constellation Gamma satellites. The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.

\subsection{The Constellation Gamma (ConGa) fleet}

\subsection{The simulated setup}

HAMAMATSU S13360-6050CS

datasheet of QE:
%http://www.hamamatsu.com/resources/pdf/ssd/s13360_series_kapd1052e.pdf

esr foil:
Please check "ESR from 3M" company. e.g.,
%http://multimedia.3m.com/mws/media/466120O/esr.pdf

\subsection{Simulation}

In order to understand how the $\gamma$ photons -- that the CubeSat is meant to detect -- interact with the matter of the satellite simulations are needed. In a simulation it is also possible to determine the optimal geometry that would lead to the best GRB detection.

The Geometry... XXX TRacking (Geant4)

\subsection{Fine tuning the optical parameters}

Most relevant parameters:
\begin{itemize}
\item absoprtion length of the scintillator material
\item scintillation yield
\end{itemize}

\section{Setup}

Size of the scintillator is, the aluminium housing thickness is, the size of the SiPM is...

Parameters of the CsI(Tl) scintillator REF

\begin{itemize}
\item Scintillation yield (Number of photons produced by given keV depleted in the scintillator)
\item The energy spectra of the produced scintillation
\item The time constant of the scintillation photon creation
\item The absorbtion length of the optical photons
\item Birks constant?
\end{itemize}

Optical parameters of the materials and surfaces:
\begin{itemize}
\item Refractive indices of all relevant materials
\item Reflection
\item The detection efficiency of the SiPM detectors
\end{itemize}

\section{Results of the simulation}
\subsection{Comparison of the results of the simulation with experiments}

The cross section for photoeffect is far the largest by far for low energy gamma photons.
The ionized nuclei and the secondary electrons generates scintillation.

ADC / energy calibration from measurement 20170829

illetve az egy chanellel: grb\_status3

\includegraphics[width=130.0mm]{images/secondary.png}

\includegraphics[width=130.0mm]{images/secondary2.png}

Also the nuclei that is ionized by the gamma produces photons.

\subsection{X-ray fluorescence}
Histogram without fluorescence, turned out in LXeEMPhysics line 140-159

Histogram with flo

\subsection{Simulation of background in space}

\subsection{Optimalization of the scintillator detectors}
\section{Conclusion}

\section{Acknowledgment}

\pagebreak

\addcontentsline{toc}{section}{References}
\begin{thebibliography}{99}
\interlinepenalty=10000

\bibitem{tgemadv} C. Shalem, R. Chechik, et al.,\\
Advances in Thick GEM-like gaseous electron multipliers—Part I: atmospheric pressure operation,\\
Nuclear Instruments and Methods in Physics Research A, vol. 558, page 475-489, 2006

\end{thebibliography}

\pagebreak

\end{document}

\begin{figure}[h!]
\centerline{
\includegraphics[width=260pt,angle=0]{images/let_setup.png}}
\caption{Az általam használt OTPC a gázrendszerével, illetve a kiolvasórendszerével együtt}
\end{figure}

Sötét anyag kutatásra jó beveztő:
https://arxiv.org/pdf/1510.02170.pdf
Nuclear physics:
https://indico.fnal.gov/conferenceDisplay.py/abstractBook?confId=8976

%%%%%%%%%%%%%%%
Alkalmazások

M. Pomorski, M. Pfutzner
M. Pomorski et al. Phys. Rev. C 90, 014311 (2014)

Micromegas-os kiolvasás J. B. R. Battat, Nucl. Instr. Meth. A 755(2014)6.

[grid???] U. Titt, V. Dagendorf et al., (Nucl. Instr. Meth. A 477 (2002) 536:	 
grids, pure TEA at low pressure, (electron counting / nano-dosimetry)

%%%%%%%%%%%%%%

Performance of an optical readout GEM-based TPC, L.M.S. Margato a...

optikai úton kiolvasott tpc-k: florian e-mailjéből

LET TPC

radon és polónium energiáira cikkek

### 2018-05-04 msc_diploma_cubesat_galgoczi.tex
l

@@
 
+The cross section for photoeffect is far the largest by far for low energy gamma photons.
+The ionized nuclei and the secondary electrons generates scintillation.
+
+\includegraphics[width=130.0mm]{images/secondary.png}
+
+\includegraphics[width=130.0mm]{images/secondary2.png}
+
+Also the nuclei that is ionized by the gamma produces photons.
+
 \subsection{Fine tuning the optical parameters}
@@
 
+\subsection{1 channel setup}
+
+\subsection{2 channel setup}
+
+\includegraphics[width=100.0mm]{images/2channel.png}
+
+\subsection{The satellite}
+
+\includegraphics[width=100.0mm]{images/satellite.png}
+
+\begin{center}
+\begin{tabular}{ |c|c|c|c|} 
+ \hline
+ Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
+ ADCS &	710	& Aluminum 6061-T6 &	50\\
+			& & Copper Electric	& 25 \\
+			& &  Glass Borosilicate 	& 25\\\hline
+ANT		&  110		& Stainless Steel 	& 50\\
+		&  & FR4 Glass-Epoxy sheet	& 50\\\hline
+AUX		& 100	& 	FR4 Glass-Epoxy sheet	& 100\\\hline
+COM	& 	90	& 	Stainless Steel 	& 2\\
+			& 	& Brass Generic		& 25\\
+			& 	& Aluminum 7075-T73		& 40\\
+			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
+EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
+			& 	& Aluminum 6061-T6		& 75\\\hline
+OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
+STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
+SP	& 	570		& Solar Panel	& 	100\\\hline
+Payload	& 	1100	& 	As you wish	& 	100\\
+ \hline
+\end{tabular}
+\end{center}
+
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
+ \hline
+%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
+Material name & &&&&&&&&&&& \\\hline
+
+Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
+Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
+%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
+Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
+Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline					
+Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
+FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
+Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
+Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline
+
+ \hline
+\end{tabular}
+\end{center}
+
+\pagebreak
+
 \section{Results of the simulation}
@@
 
-The cross section for photoeffect is far the largest by far for low energy gamma photons.
-The ionized nuclei and the secondary electrons generates scintillation.
+%ADC / energy calibration from measurement 20170829 illetve az egy chanellel: grb\_status3
 
-ADC / energy calibration from measurement 20170829
+1 channel read out:
 
-illetve az egy chanellel: grb\_status3
+\includegraphics[width=100.0mm]{images/irradiation.png}
 
-\includegraphics[width=130.0mm]{images/secondary.png}
+\includegraphics[width=40.0mm]{images/positions.png}
 
-\includegraphics[width=130.0mm]{images/secondary2.png}
+The experimental results:
 
-Also the nuclei that is ionized by the gamma produces photons.
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
+ \hline
+  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+  Pos. of main peak & 0.642 & 0.664 & & 70.7 & 0.743 & & 0.598 & &  \\ 
+ \hline
+\end{tabular}
+\end{center}
+
+The parameters set in the simulation: reflectivity: 0.995 and absoprtion length of
+40 cm:
+
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
+ \hline
+  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+  Pos. of main peak & 0.3389 & 0.3256 & 0.3355 & 0.3521 & 0.3555 & 0.3522 & 0.2060 & 1 & 0.203  \\ 
+ \hline
+\end{tabular}
+\end{center}
+
+The parameters set in the simulation: reflectivity: 0.995 and absoprtion length of 50 cm
+
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
+ \hline
+ Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+ Pos. of main peak & 0.4013 & 0.3917 & 0.3981 & 0.4045 & 0.4172 & 0.4140 & 0.2580 & 1 & 0.2739\\ 
+ \hline
+\end{tabular}
+\end{center}
+
+Reflectivity of 0.997 and abs. length of 60 cm
+
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
+ \hline
+  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+  Pos. of main peak & 0.4588 & 0.4587 & 0.4697 & 0.4734 & 0.4700 & 0.4737 & 0.3388 & 1 & 0.3365  \\ 
+ \hline
+\end{tabular}
+\end{center}
 

### 2018-05-06 msc_diploma_cubesat_galgoczi.tex
text

@@
 \vspace{1.5cm}
-\begin{figure}[H]
-\centering
-\begin{tabular}{ >{\centering\arraybackslash}m{2in}  >{\centering\arraybackslash}m{2.5in}  }
-
-\includegraphics[width=53.0mm]{images/regard.jpg}
-\end{tabular}
-\end{figure}
 
@@
 \centering
-\begin{tabular}{ >{\centering\arraybackslash}m{2in}  >{\centering\arraybackslash}m{2.5in}  }
 
-\includegraphics[width=45.0mm]{images/elte.png} \parbox{0pt}{\rule{0pt}{2ex+\baselineskip}} &
-\hspace{0.2 cm}
-\includegraphics[width=40.0mm]{images/wigner.png}
-\end{tabular}
+\includegraphics[width=80.0mm]{images/elte.png}  
 \end{figure}
@@
 
-\vspace{0.1 cm}
+\vspace{4 cm}
 \end{center}
@@
 \centerline{ Témavezetők: } \\
-\centerline{ Conseil Européen pour la Recherche Nucléaire (CERN)}
+\centerline{ Norbert Werner (ELTE)}
 \end{tabular}
@@
 \vspace{2.5 cm}
-\large \textbf {2016}\\
+\large \textbf {2018}\\
 \end{center}
@@
 
-\subsection{2 channel setup}
+\includegraphics[width=150.0mm]{images/irradiation.png}
 
-\includegraphics[width=100.0mm]{images/2channel.png}
+\subsection{2 channel read out setup}
+
+\begin{figure}[H]
+\includegraphics[width=160.0mm]{images/2channel.png}
+\caption{Simulation of 100 $\gamma$s emitted from the source.
+The blue lines represent the track of the $\gamma$s and the green lines represent the track of the optical photons created by scintillation.
+Only the photons that were detected are drawn.}
+\end{figure}
 
@@
 
+\begin{table}
 \begin{center}
@@
 \end{center}
+\caption{The mass ratio of materials that are used for the satellite}
+\end{table}
+
+\begin{table}
 
@@
 Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline
-
- \hline
 \end{tabular}
 \end{center}
+\caption{The chemical composition of materials that are used for the satellite}
+\end{table}
 
@@
 
-\includegraphics[width=100.0mm]{images/irradiation.png}
-
-\includegraphics[width=40.0mm]{images/positions.png}
+\includegraphics[width=80.0mm]{images/positions.png}
 
@@
 
-\subsection{Simulation of background in space}
+\subsection{Simulation of the cosmic background in space}
 
 \subsection{Optimalization of the scintillator detectors}
+
+\pagebreak
 \section{Conclusion}
+
+In order to simulate how the XXX CubeSat would interact with the cosmic background and how sensitive it would be to the GRBs that it is designed to investigate a Geant4 simulation was built.
+
+As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the particle detector of the satellite -- was implemented in Geant4.
+The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs that was used to read out the scintillator.
+
+Secondly, the CAD model of the satellite was exported to Geant4.
+The body of the satellite was divided into 8 modules.
+The chemical components of these modules were included in the simulation.
+The scintillator was placed on the side of the satellite.
+
+Thirdly, the effect of cosmic radiation was invastigated by obtaining the energy spectra of cosmic protons and electrons at the XXX altitude of XXX.
+The satellite was radiated by these particles in Geant4 from all directions to investigate how large the signal of these particles would be.
+This needs to be minimalized as it versenyez with the signal of gamma particles from GRBs.
+
+Finally, the $\gamma$ absorption of the satellite was invastigated.
+
+\pagebreak
 

### 2018-05-07 msc_diploma_cubesat_galgoczi.tex
lool
aa

@@
 
+\includegraphics[width=150.0mm]{images/satellite_rad.png}
+
 \begin{table}
@@
 			& &  Glass Borosilicate 	& 25\\\hline
-ANT		&  110		& Stainless Steel 	& 50\\
-		&  & FR4 Glass-Epoxy sheet	& 50\\\hline
-AUX		& 100	& 	FR4 Glass-Epoxy sheet	& 100\\\hline
 COM	& 	90	& 	Stainless Steel 	& 2\\
@@
 
+In order to include the resonances in the cross section of the hadron-hadron interactions, additional physics models are needed to be included in the simulation.
+The signal induced by these resonances might affect the measurement of the protons.
 \subsection{Optimalization of the scintillator detectors}

### 2018-05-11 msc_diploma_cubesat_galgoczi.tex
update

--- 2018-05-06 msc_diploma_cubesat_galgoczi.tex
@@
 %\vspace{0.5 cm}
-\textit{\textbf{Galgóczi Gábor$^{*}$, Fizikus MSc szak, 2. évfolyam}}\\
+\textit{\textbf{Galgóczi Gábor$^{*}$, Fizikus MSc szak, 3. évfolyam}}\\
 Eötvös Loránd Tudományegyetem, Természettudományi Kar\\
@@
 
-\subsection{Fine tuning the optical parameters}
-
-Most relevant parameters:
-\begin{itemize}
-\item absoprtion length of the scintillator material
-\item scintillation yield
-\end{itemize}
-
 \section{Setup}
@@
 \includegraphics[width=150.0mm]{images/irradiation.png}
+
+The $\gamma$ source that was used to test the experimental setup was choosen to be an $^{241}Am$.
+The reason for this is that the peak of energy spectrum of the $\gamma$ photons from GRBs is at 50 keV which is very close to the peak of the $^{241}Am$ that is 59.5 keV.
+The activity of the source at the time of the experiment was 471 kBq.
+The source was collimated to a beam that hit the surface of the scintillator on a circle with a radius of 10 mm.
+The distance of the source from the scintillator was 13.5 mm.
+Therefore the number of $\gamma$s that hit the scintillator, the Al and Pb sheets above it was:
+$$471 kBq \cdot \frac{s}{s}$$
+
+\subsection{Fine tuning the optical parameters}
+
+Most relevant parameters:
+\begin{itemize}
+\item absoprtion length of the scintillator material
+\item reflection of the ESR (Enchanced Specular Reflector) tape the is wrapped around the scintillator 
+\item scintillation yield
+\end{itemize}
 

### 2018-05-12 msc_diploma_cubesat_galgoczi.tex
update

@@
 
+\begin{figure}[htbp]
+ \centering % \begin{center}/\end{center} takes some additional vertical space
+ \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
+ \qquad
+ \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \end{figure}
+
+\begin{figure}
+\includegraphics[width=130.0mm]{images/1channelelectronics.png}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=130.0mm]{images/tap1channel.png}
+\caption{\label{fig:1channeltape} The MPPC is fixed to the scintillator with valqua tape}
+\end{figure}
+
 Size of the scintillator is, the aluminium housing thickness is, the size of the SiPM is...
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=130.0mm]{images/2channelsetup.png}
+\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
+\end{figure}
+
+\includegraphics[width=130.0mm]{images/2channelelectronics.png}
+
 \begin{figure}[H]
+\centering
 \includegraphics[width=160.0mm]{images/2channel.png}
@@
 
-\includegraphics[width=100.0mm]{images/satellite.png}
+\begin{figure}[htbp]
+ \centering % \begin{center}/\end{center} takes some additional vertical space
+ \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
+ \qquad
+ \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \end{figure}
 
+\begin{figure}
 \includegraphics[width=150.0mm]{images/satellite_rad.png}
+\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
+\end{figure}
 
@@
 
+\begin{figure}
+\centering
 \includegraphics[width=80.0mm]{images/positions.png}
+\caption{The positions of irradiation for the investigation of the response of the scintillator}
+\end{figure}
 

### 2018-05-12 msc_diploma_cubesat_galgoczi.tex

@@
 
+\subsection{Gamma-ray bursts}
+
+Gamma-ray bursts (GRBs) [1, 2, 3, 4, 5, 6, 7, 8, 9] have been studied already about four decades, nonetheless their origin is still not fully understood.
+They are one of the most extreme explosive events ever observed.
+In spite of tremendous effort and numerous observations there are still open questions concerning their detailed physics.
+GRBs were discovered in years 1967–73 by military Vela satellites and later reported to the scientific community in early seventies [10, 11].
+They occur roughly once per day and are characterized by flashes of $\gamma$-rays typically lasting from a fraction of a second to thousands of seconds, typically in the energy range from several keV to several MeV, however $\gamma$-rays of energy >1 GeV associated with GRBs were detected as well.
+A GRB event outshines any other gamma-ray source on the sky.
+It has been found that the duration distribution of their $\gamma$-ray prompt emission is bimodial [12] which suggested that there were two groups of GRBs.
+Later, based on more observations, it has been confirmed that these two GRB groups were two distinct astrophysical populations [12, 13, 14, 15, 16,17]: I.
+so called long GRBs (LGRBs) with softer spectrum and with prompt $\gamma$-ray emission $\geqslant$2 s that were identified to be gravitational collapses of massive stars due to their association with type Ic core-collapse supernovae, and II.
+so called short GRBs (SGRBs) with harder spectrum and with prompt $\gamma$-ray emission $\leqslant$2 s originating in merger of two compact objects such as neutron star - neutron star (NS-NS) or neutron star - black hole (NS-BH) [18].
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/Gamma_ray_burst.jpg}
+\caption{The life cycle of a massive star. When fusion stops the collapsing star releases energy in the form of jets observed as a gamma-ray burst}
+\end{figure}
+
+It was proposed that GRBs were created in collisions of highly relativistic outflow of the accelerated jetted matter [19, 20].
+In many cases it was found that the prompt $\gamma$-ray emission is followed by longer-lasting afterglow in soft X-ray, optical or radio waves [21, 22] explained as a result of the propagation of a relativistic shockwave through the circumburst medium.
+The suggestion that GRBs lie at cosmological distances [23] was confirmed by numerous observations and it was found that their redshifts are up to z=9.4 with $\langle$ z $\rangle\approx$0.5 for SGRBs and $\langle$z$\rangle \approx$2.0 for LGRBs [18].
+The energy content 51 released in a GRB is $\sim$10 erg.
+In some cases of LGRBs there was observed supernova component in the lightcurve or in the spectrum of its afterglow, peaking $\sim$2 weeks after the initial trigger [24, 25, 26].
+LGRBs are associated with the brightest regions of galaxies and with the most massive stars [27].
+The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5].
+The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 [28].
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/GRB_BATSE_12lightcurves.png}
+\caption{The light curves of 12 gamma-ray bursts observed by BATSE.
+The diversity of the curves is extraordinary.
+Events with a length from millisecond to a second exist either with smooth or highly variable curves.}
+\end{figure}
+
+Observations suggest that SGRBs arise from old astrophysical populations.
+The beaming angles for SGRBs jets seems to be from $\sim$5 to > 25 [5, 29, 30].
+The model that they originate in the merger of two NS has been recently confirmed by the detection of the gravitational wave (GW) signal by LIGO / Virgo collaboration 1, 2.
+This GW signal was accompanied with a SGRB detected by the Fermi /Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy [31, 32, 33].
+In case of SGRBs a kilonova/macronova can be observed.
+It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process [34].
+
+\subsection{Open questions on gamma-ray bursts}
+
+In spite of great theoretical and observational successes over the last four decades, many key questions remain about the physics of GRBs.
+For a detailed review see [3, 4, 6, 35].
+Some of these key questions are following.
+
+Central engine: it is usually considered that as a result of the core collapse of a massive star or as a result of a merger of two compact objects there is a newborn BH created.
+Some models also consider that instead of a BH, a rapidly rotating NS with strong surface magnetic field (magnetar), B$\geqslant	$10$^{11}$ T, is formed.
+Another suggested possibility is a formation of a never observationally confirmed quark star composed of quark matter.
+The particle acceleration mechanism in the relativistic shocks and the microphysics of the shocks is a major open issue in the GRB physics. 
+GRB jet composition: it is still debated if the GRB outflow is baryonic or magnetic field (Poynting flux) dominated.
+The jet composition is tied to whether GRBs can accelerate protons to ultra-high energies and produce Ultra-High Energy Cosmic Rays (UHECRs) and high energy neutrinos.
+The models which expect GRBs to be sources of UHECR and high energy neutrinos invoke a baryon-dominated outflow.
+Radiation mechanism: the prompt emission of GRBs is non-thermal, smoothly-joint broken-power-law called “Band” function.
+The emission is required to be produced by a population of particles, e.g.
+leptons, with a power law distribution of their energies.
+The main assumed mechanisms are synchrotron radiation, Synchrotron Self-Compton radiation, and Compton up-scattering of thermal photons however it is difficult to identify the correct radiation mechanism with the current available
+data.
+First stars (Pop III): what is the expected signature of GRBs originating in the death of the first metal-free massive stars at high redshift?
+It was estimated that the mass of the BH at the center of the collapsar of Pop III star is a factor of ten larger and Pop III GRBs may thus tend to have larger durations than those of ordinary Pop I and Pop II GRBs [36].
+Classification: there are cases of GRBs which do not exactly fit in the usual short/long classification.
+For example the ultra-long GRBs or short GRBs with soft extended emission. Next question is what is
+the nature of the precursors in some of the GRB light curves?
+Recent detection of the electromagnetic (EM) signal of the short GRB 170817A [37] associated with a GW signal GW170817 produced by a binary neutron star (BNS) merger [32] marks a milestone in the multi-messenger research of GRBs and means a great importance of the efforts of searching for EM counterparts to GW sources with spaceborn instruments.
+The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A.
+Approximately 1.7 prior to this GRB, LIGO-Virgo detector network observed a GW signal GW170817 at 12:41:04.4 UTC which originated from a BNS inspiral.
+The source was localized 9/89within a sky region of 28 deg 2 (90 \% probability), which was the most precisely localized GW signal yet.
+An extensive observing campaign was launched across the electromagnetic spectrum [33] leading to the discovery of a bright optical transient in NGC 4993.
+Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL [38], Chandra X-ray Observatory [39], Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected [40].
+Some models predict also EM signal from BBH coalescence, for example [41, 42].
+More detections of EM counterpart to GW sources and kilonovae are indeed essential for better understanding of these phenomena and this proposed mission has a great potential to bring new and valuable observational data.
+After the upgrades of LIGO, following the finished observing run O2, there will be O3 run scheduled to start in 2018.
+Further observing runs are expected after next improve of the sensitivity.
+Designed sensitivity is aimed to be achieved in 2021.
+The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s [43].
+Therefore, more GW detections are expected during the operation of this proposed mission.
+
+\subsection{Particle detectors in space}
+
+Various detector types has been used or are planned for space instruments for example gas-filled detectors like proportional counters and Geiger counters; scintillation detectors like inorganic crystal scintillators, e.g.
+NaI(Tl) or CsI(Tl), and plastic scintillators; semiconductor devices like, e.g.
+cryogenically cooled germanium, Cadmium Zinc Telluride (CZT) or Silicon Drift Detector (SDD) technique.
+Other types of detectors used in space missions are Compton scatter telescopes or pair production telescopes.
+Table 3 lists detector technologies capable of detecting GRBs in hard X-ray and gamma-ray range employed in previous and current major instruments.
+For an extensive review of hard X-ray / soft gamma-ray experiments and missions see [47].
+
+\subsection{Current missions observing gamma-ray bursts}
+
+Several spaceborn instruments and ground-based observatories are currently operating or are planed in
+order to bring more detailed observations of GRBs to better understand their nature. Their overview
+and comparison with the required specification on our proposed mission is given in following
+subsections.
+Our project will benefit from large field of view (FoV) and high localization accuracy. It will provide
+full-sky FoV and due to the advantage of using multiple satellites the occulted area by the Earth will
+be eliminated.
+The expected localization accuracy will be from $\sim$10' to degrees depending on the flux and duration of a GRB.
+This is not achieved by any of the current GRB missions.
+In the current missions either the large FoV or precise localization accuracy is accomplished.
+The large FoV instruments, e.g.
+INTEGRAL/SPI-ACS or Fermi/GBM, have either no localization capability or the localization accuracy is of the order of several degrees.
+On the other hand the current instruments providing localization accuracy of the order of arcmin have limited FoV, e.g.
+Swift/BAT or
+AGILE/Super-AGILE.
+Another advantage of our proposed mission is that the cost is only a fraction of the cost of a big
+satellite missions, e.g. like SVOM, and the concept of multiple cubesats allows higher flexibility in
+terms of extending the fleet by more satellites as well as allows replenishment of failed satellites.
+
+Fermi 7 [44, 45, 66] was launched in 2008 and the main instruments are the Large Area Telescope (LAT) and the Gamma-ray Burst Monitor. 
+Neil Gehrels Swift Observatory (Swift) 8 [64, 67] was launched in 2005 and the main instruments are
+Burst Alert Telescope (BAT), X-ray Telescope (XRT), and UV/Optical Telescope (UVOT).
+INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 [57, 58, 68, 69] was launched in
+2002 Among several instruments on board INTEGRAL the ones which detect most of GRBs are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the Imager on Board the Integral Satellite (IBIS).
+Wind/Konus 10 [70] was launched in 1994 and its still active GRB instrument is Konus.
+Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 /Super-AGILE [48, 71] was launched in
+2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
+CALorimetric Electron Telescope (CALET) 12 [52, 72, 73] / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
+
+Monitor of All-sky X-ray Image (MAXI) 13 [60, 74 ], started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
+Gamma-ray Burst Polarimeter POLAR 14 [61, 75], was launched in 2016 and is dedicated to the measurement of GRB polarization.
+Lomonosov 15 /BDRG [59, 76], was launched in 2016. The BDRG instrument on board detected several GRBs.
+The Hard X-ray Modulation Telescope (Insight-HXMT) 16 [56, 77], was launched in 2017.
+It has on board the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
+ASTROSAT 17 [49, 78, 79], was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
+Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 [62, 80, 81], was launched in 2002.
+It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
+The energy range, FoV and localization accuracy for the instruments of the current missions which observe GRBs is summarized in Table 4.
+Figure 3 shows the FoV vs.
+localization accuracy of the current instruments which detect GRBs.
+For comparison the specification of this project is shown as
+well.
+
+\subsection{Currently operating GRB collection and alert networks}
+
+Our project can potentially contribute to some of the currently operating GRB collection and alertnetworks such as the following ones:
+The InterPlanetary Network (IPN) 27 [97, 98] which derives the positions of fast gamma-ray transients of all kinds by triangulation.
+Numerous spacecraft and instruments participate in the network at the Earth’s orbit as well as in the interplanetary space.
+It detects about 350/year.
+The Gamma-ray Coordinates Network (Transient Astronomy Network) (GCN/TAN) 28 provides information about GRBs in real-time to the world community.
+The network provides the real-time (and near real-time) distribution of GRB locations, images, spectra, and lightcurves detected by various spacecraft and the distribution of follow-up observation reports.
+The Global Relay of Observatories Watching Transients Happen (GROWTH) 29 is an international scientific collaborative project studying the astronomical transients.
+
+\subsection{Current GRB Follow-up observations}
+
+This cubesat project will provide high precision localization accuracy of GRBs allowing efficient follow-up observations by existing ground based observatories.
+There are several observatories world-wide to perform photometric or spectroscopic observations of GRB afterglows, for example:
+The Mobile Astronomical System of TElescope Robots (MASTER) 30 [99] is a global network of robotic telescopes for very fast positioning and follow up of GRBs.
+The Burst Optical Observer and Transient Exploring System (BOOTES) network of robotic telescopes for follow up observations of GRBs.
+31 [100] is a world wide The Robotic Optical Transient Search Experiment (ROTSE) 32 [101] are telescopes which operate at
+sites around the world and follow GRBs.
+Pi of the Sky 33 [102] is a system of detectors designed for continuous observation of night sky looking for optical flashes of astrophysical origin, in particular for GRBs.
+Several other telescopes and observatories which provide measurements in optical, infra-red or radio bands are also, e.g.: Gamma-Ray Burst Optical/Near-Infrared Detector (GROND) 34 , the Palomar 60 inch telescope 35 , Rapid Eye Mount (REM) 36 , Livermore Optical Transient Imaging System (Super- LOTIS) 37 , Télescopes à Action Rapide pour les Objets Transitoires (TAROT) 38 , Gran Telescopio Canarias (GTC) 39 , ESO Very Large Telescope (VLT) 40 , Nordic Optical Telescope (NOT) 41 , Observatorio Astronómico Nacional on the Sierra de San Pedro Mártir 42 , Cerro Tololo Inter-American Observatory (CTIO) 43 , Telescopio Nazionale Galileo (TNG) 44 , Gao-Mei-Gu (GMG) station of Yunnan Observatories 45 , Observatorio de Sierra Nevada (OSN) 46 , United Kingdom Infrared Telescope (UKIRT) 47 , Very Large Array (VLA) 48 , Atacama Large Millimeter/Submillimeter Array (ALMA) 49 , James Clerk Maxwell Telescope 50 , Arcminute Microkelvin Imager which robotically triggers on Swift GRBs (AMI-GRB) 51 .
+
 \subsection{Aim of the simulation}
+
+\subsection{The Constellation Gamma (ConGa) fleet}
 
@@
 The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.
-
-\subsection{The Constellation Gamma (ConGa) fleet}
 

### 2018-05-14 msc_diploma_cubesat_galgoczi.tex
added

@@
 The distance of the source from the scintillator was 13.5 mm.
+Therefore the solid angle of the part of the whole sphere where $\gamma$s could be detected was
+$$\Theta = 2 \pi (1-cos(\theta)) = 1.234 sr$$
+
  Therefore the number of $\gamma$s that hit the scintillator, the Al and Pb sheets above it was:
-$$471 kBq \cdot \frac{s}{s}$$
+$$A = \frac{1.234}{4 \pi} \cdot 471 kBq = 46.25 kBq$$
 
@@
 
+\pagebreak
+
 \subsection{2 channel read out setup}
@@
 \centering
-\includegraphics[width=130.0mm]{images/2channelsetup.png}
+\includegraphics[width=130.0mm]{images/2channelsetup.png}[H!]
 \caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
@@
 \subsection{Comparison of the results of the simulation with experiments}
+\subsubsection{Calibration of the position dependence}
 
@@
 \end{center}
+
+\pagebreak
+
+\subsubsection{Calibration of photon yield}
+
+In the simulation 3.6 million $\gamma$s were simulated.
+The measurement took 240 s.
+Therefore the number of photons emitted by the source was $\sim$ 11.0 million.
+The amplitude of the peaks in the energy spectrum of signal obtained by the MPPC depends mostly on three parameters.
+The absorption length of the scintillation light in the scintillator, the reflectivity of the surface and the scintillation photon yield of the scintillator.
+In order to obtain the histogram that we would measure by the MPPC, the histogram obtained by the simulation had to be scaled up both in amplitude and energy.
+(The introduction of an offset was not needed as the origin point of the histogram obtained in the measurements was shifted to zero energy.)
 

### 2018-05-15 msc_diploma_cubesat_galgoczi.tex
ii

@@
 It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process [34].
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/grb_spectra.png}
+\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\end{figure}
 
@@
 \section{Results of the simulation}
+
 \subsection{Comparison of the results of the simulation with experiments}
+
+\subsubsection{X-ray fluorescence}
+
+Histogram without fluorescence, turned out in LXeEMPhysics line 140-159
+
+Histogram with flo
+
 \subsubsection{Calibration of the position dependence}
@@
 
-\subsection{X-ray fluorescence}
-Histogram without fluorescence, turned out in LXeEMPhysics line 140-159
+\begin{figure}
+\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
+\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
+\end{figure}
 
-Histogram with flo
+The energy bins had to be scaled up by a factor of 2.4 to match the experimental results. The amplitude had to be scaled up by a factor of 26.2.
+
+\pagebreak
 
@@
 The signal induced by these resonances might affect the measurement of the protons.
-\subsection{Optimalization of the scintillator detectors}
+
+Protons
+'Apogee: 500.0 km'
+'Perigee: 500.0 km'
+'Inclination: 89.0 deg'
+
+Electrons
+'Trapped electron model: AE-8 MIN'
+%'Energy','MeV','Energy'
+%'IFlux','cm^-2 s^-1','Integral Flux'
+%'DFlux','cm^-2 s^-1 MeV^-1','Differential Flux'
 
@@
 Nuclear Instruments and Methods in Physics Research A, vol. 558, page 475-489, 2006
+
+\bibitem{grb_spectra} Gamma-Ray Bursts and Fast Transients
+Multi-wavelength Observations and Multi-messenger Signals,\\
+R. Willingale, P. Mészáros
+%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf
 

### 2018-05-16 msc_diploma_cubesat_galgoczi.tex
images

@@
 
+The main aim of the paper, therefore this thesis is to optimize the scintillators of the CubeSats (miniaturized satellites) in the Constellation Gamma satellites.
+It is not known which would be the best detector configuration for the detection of GRBs.
+In the
+
+ The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.
+
 \subsection{Gamma-ray bursts}
 
-Gamma-ray bursts (GRBs) [1, 2, 3, 4, 5, 6, 7, 8, 9] have been studied already about four decades, nonetheless their origin is still not fully understood.
+Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} have been studied already about four decades, nonetheless their origin is still not fully understood.
 They are one of the most extreme explosive events ever observed.
 In spite of tremendous effort and numerous observations there are still open questions concerning their detailed physics.
-GRBs were discovered in years 1967–73 by military Vela satellites and later reported to the scientific community in early seventies [10, 11].
+GRBs were discovered in years 1967–73 by military Vela satellites and later reported to the scientific community in early seventies \cite{grb5}.
 They occur roughly once per day and are characterized by flashes of $\gamma$-rays typically lasting from a fraction of a second to thousands of seconds, typically in the energy range from several keV to several MeV, however $\gamma$-rays of energy >1 GeV associated with GRBs were detected as well.
 A GRB event outshines any other gamma-ray source on the sky.
-It has been found that the duration distribution of their $\gamma$-ray prompt emission is bimodial [12] which suggested that there were two groups of GRBs.
-Later, based on more observations, it has been confirmed that these two GRB groups were two distinct astrophysical populations [12, 13, 14, 15, 16,17]: I.
+It has been found that the duration distribution of their $\gamma$-ray prompt emission is bimodial \cite{grb6} which suggested that there were two groups of GRBs.
+Later, based on more observations, it has been confirmed that these two GRB groups were two distinct astrophysical populations \cite{grb6,grb7,grb8}: I.
 so called long GRBs (LGRBs) with softer spectrum and with prompt $\gamma$-ray emission $\geqslant$2 s that were identified to be gravitational collapses of massive stars due to their association with type Ic core-collapse supernovae, and II.
-so called short GRBs (SGRBs) with harder spectrum and with prompt $\gamma$-ray emission $\leqslant$2 s originating in merger of two compact objects such as neutron star - neutron star (NS-NS) or neutron star - black hole (NS-BH) [18].
+so called short GRBs (SGRBs) with harder spectrum and with prompt $\gamma$-ray emission $\leqslant$2 s originating in merger of two compact objects such as neutron star - neutron star (NS-NS) or neutron star - black hole (NS-BH) \cite{grb9}.
 
@@
 
-It was proposed that GRBs were created in collisions of highly relativistic outflow of the accelerated jetted matter [19, 20].
-In many cases it was found that the prompt $\gamma$-ray emission is followed by longer-lasting afterglow in soft X-ray, optical or radio waves [21, 22] explained as a result of the propagation of a relativistic shockwave through the circumburst medium.
-The suggestion that GRBs lie at cosmological distances [23] was confirmed by numerous observations and it was found that their redshifts are up to z=9.4 with $\langle$ z $\rangle\approx$0.5 for SGRBs and $\langle$z$\rangle \approx$2.0 for LGRBs [18].
+It was proposed that GRBs were created in collisions of highly relativistic outflow of the accelerated jetted matter \cite{grb10}.
+In many cases it was found that the prompt $\gamma$-ray emission is followed by longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11} explained as a result of the propagation of a relativistic shockwave through the circumburst medium.
+The suggestion that GRBs lie at cosmological distances \cite{grb12} was confirmed by numerous observations and it was found that their redshifts are up to z=9.4 with $\langle$ z $\rangle\approx$0.5 for SGRBs and $\langle$z$\rangle \approx$2.0 for LGRBs [18].
 The energy content 51 released in a GRB is $\sim$10 erg.
-In some cases of LGRBs there was observed supernova component in the lightcurve or in the spectrum of its afterglow, peaking $\sim$2 weeks after the initial trigger [24, 25, 26].
-LGRBs are associated with the brightest regions of galaxies and with the most massive stars [27].
+In some cases of LGRBs there was observed supernova component in the lightcurve or in the spectrum of its afterglow, peaking $\sim$2 weeks after the initial trigger \cite{grb13}.
+LGRBs are associated with the brightest regions of galaxies and with the most massive stars \cite{grb14}.
 The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5].
-The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 [28].
+The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 \cite{grb15}.
 
@@
 Observations suggest that SGRBs arise from old astrophysical populations.
-The beaming angles for SGRBs jets seems to be from $\sim$5 to > 25 [5, 29, 30].
+The beaming angles for SGRBs jets seems to be from $\sim$5 to > 25 \cite{grb16}.
 The model that they originate in the merger of two NS has been recently confirmed by the detection of the gravitational wave (GW) signal by LIGO / Virgo collaboration 1, 2.
-This GW signal was accompanied with a SGRB detected by the Fermi /Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy [31, 32, 33].
+This GW signal was accompanied with a SGRB detected by the Fermi /Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}.
 In case of SGRBs a kilonova/macronova can be observed.
-It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process [34].
+It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.
 
@@
 In spite of great theoretical and observational successes over the last four decades, many key questions remain about the physics of GRBs.
-For a detailed review see [3, 4, 6, 35].
+For a detailed review see \cite{grb19}.
 Some of these key questions are following.
@@
 First stars (Pop III): what is the expected signature of GRBs originating in the death of the first metal-free massive stars at high redshift?
-It was estimated that the mass of the BH at the center of the collapsar of Pop III star is a factor of ten larger and Pop III GRBs may thus tend to have larger durations than those of ordinary Pop I and Pop II GRBs [36].
+It was estimated that the mass of the BH at the center of the collapsar of Pop III star is a factor of ten larger and Pop III GRBs may thus tend to have larger durations than those of ordinary Pop I and Pop II GRBs \cite{grb20}.
 Classification: there are cases of GRBs which do not exactly fit in the usual short/long classification.
@@
 the nature of the precursors in some of the GRB light curves?
-Recent detection of the electromagnetic (EM) signal of the short GRB 170817A [37] associated with a GW signal GW170817 produced by a binary neutron star (BNS) merger [32] marks a milestone in the multi-messenger research of GRBs and means a great importance of the efforts of searching for EM counterparts to GW sources with spaceborn instruments.
+Recent detection of the electromagnetic (EM) signal of the short GRB 170817A \cite{grb21} associated with a GW signal GW170817 produced by a binary neutron star (BNS) merger \cite{grb17} marks a milestone in the multi-messenger research of GRBs and means a great importance of the efforts of searching for EM counterparts to GW sources with spaceborn instruments.
 The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A.
@@
 The source was localized 9/89within a sky region of 28 deg 2 (90 \% probability), which was the most precisely localized GW signal yet.
-An extensive observing campaign was launched across the electromagnetic spectrum [33] leading to the discovery of a bright optical transient in NGC 4993.
-Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL [38], Chandra X-ray Observatory [39], Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected [40].
-Some models predict also EM signal from BBH coalescence, for example [41, 42].
+An extensive observing campaign was launched across the electromagnetic spectrum leading to the discovery of a bright optical transient in NGC 4993.
+Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL \cite{grb22}, Chandra X-ray Observatory \cite{grb23}, Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected \cite{grb24}.
+Some models predict also EM signal from BBH coalescence, for example \cite{grb25}.
 More detections of EM counterpart to GW sources and kilonovae are indeed essential for better understanding of these phenomena and this proposed mission has a great potential to bring new and valuable observational data.
@@
 Designed sensitivity is aimed to be achieved in 2021.
-The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s [43].
+The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s \cite{grb26}.
 Therefore, more GW detections are expected during the operation of this proposed mission.
@@
 Table 3 lists detector technologies capable of detecting GRBs in hard X-ray and gamma-ray range employed in previous and current major instruments.
-For an extensive review of hard X-ray / soft gamma-ray experiments and missions see [47].
+For an extensive review of hard X-ray / soft gamma-ray experiments and missions see \cite{grb30}.
 
@@
 
-Fermi 7 [44, 45, 66] was launched in 2008 and the main instruments are the Large Area Telescope (LAT) and the Gamma-ray Burst Monitor. 
-Neil Gehrels Swift Observatory (Swift) 8 [64, 67] was launched in 2005 and the main instruments are
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/fovvsloc.png}
+\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\end{figure}
+
+Fermi 7 \cite{grb28} was launched in 2008 and the main instruments are the Large Area Telescope (LAT) and the Gamma-ray Burst Monitor. 
+Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 and the main instruments are
 Burst Alert Telescope (BAT), X-ray Telescope (XRT), and UV/Optical Telescope (UVOT).
-INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 [57, 58, 68, 69] was launched in
+INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 \cite{grb32} was launched in
 2002 Among several instruments on board INTEGRAL the ones which detect most of GRBs are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the Imager on Board the Integral Satellite (IBIS).
-Wind/Konus 10 [70] was launched in 1994 and its still active GRB instrument is Konus.
-Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 /Super-AGILE [48, 71] was launched in
+Wind/Konus 10 \cite{grb33} was launched in 1994 and its still active GRB instrument is Konus.
+Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 /Super-AGILE \cite{grb34} was launched in
 2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
-CALorimetric Electron Telescope (CALET) 12 [52, 72, 73] / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
+CALorimetric Electron Telescope (CALET) 12 \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
 
-Monitor of All-sky X-ray Image (MAXI) 13 [60, 74 ], started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
-Gamma-ray Burst Polarimeter POLAR 14 [61, 75], was launched in 2016 and is dedicated to the measurement of GRB polarization.
-Lomonosov 15 /BDRG [59, 76], was launched in 2016. The BDRG instrument on board detected several GRBs.
-The Hard X-ray Modulation Telescope (Insight-HXMT) 16 [56, 77], was launched in 2017.
+Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
+Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of GRB polarization.
+Lomonosov 15 /BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
+The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39}, was launched in 2017.
 It has on board the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
-ASTROSAT 17 [49, 78, 79], was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
-Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 [62, 80, 81], was launched in 2002.
+ASTROSAT 17 \cite{grb40}, was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
+Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 \cite{grb41}, was launched in 2002.
 It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
@@
 Our project can potentially contribute to some of the currently operating GRB collection and alertnetworks such as the following ones:
-The InterPlanetary Network (IPN) 27 [97, 98] which derives the positions of fast gamma-ray transients of all kinds by triangulation.
+The InterPlanetary Network (IPN) 27 \cite{grb42} which derives the positions of fast gamma-ray transients of all kinds by triangulation.
 Numerous spacecraft and instruments participate in the network at the Earth’s orbit as well as in the interplanetary space.
@@
 There are several observatories world-wide to perform photometric or spectroscopic observations of GRB afterglows, for example:
-The Mobile Astronomical System of TElescope Robots (MASTER) 30 [99] is a global network of robotic telescopes for very fast positioning and follow up of GRBs.
+The Mobile Astronomical System of TElescope Robots (MASTER) 30 \cite{grb43} is a global network of robotic telescopes for very fast positioning and follow up of GRBs.
 The Burst Optical Observer and Transient Exploring System (BOOTES) network of robotic telescopes for follow up observations of GRBs.
-31 [100] is a world wide The Robotic Optical Transient Search Experiment (ROTSE) 32 [101] are telescopes which operate at
+31 \cite{grb44} is a world wide The Robotic Optical Transient Search Experiment (ROTSE) 32 [101] are telescopes which operate at
 sites around the world and follow GRBs.
@@
 
-\subsection{Aim of the simulation}
+\subsection{The CAMELOT satellite}
 
-\subsection{The Constellation Gamma (ConGa) fleet}
+There would most likely be four scintillators on the CAMELOT satellite.
+On two neighbouring sides of the satellite have two scintillators each.
+The scintillator will have a case either from aluminium or carbon fibre.
 
-The main aim of the paper, therefore this thesis is to optimize the scintillators of the CubeSats (miniaturized satellites) in the Constellation Gamma satellites.
-The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/satellite_modules.png}
+\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\end{figure}
+
+\begin{itemize}
+\item The CubeSat platform has the following Sub-systems level elements, Figure 5 shows the sub-systems
+of the CubeSat platform.
+\item On-Board Computer [OBC] is responsible for control all the satellite’s sub-systems. OBC collects housekeeping and payload data and archives them in its internal storage.
+\item Electrical Power System [EPS] is responsible for managing primary and secondary power sources and distributing power at appropriate voltage levels to on-board subsystems.
+\item COM UHF Transceiver [COM] provides an RF communication link between the Ground Segment and the satellite.
+The COM codes the received messages from the OBC and transmits to the Ground Segment.
+Furthermore, the COM decodes the received RF messages from the Ground Segment and transmits to the OBC.
+\item Attitude Determination and Control System [ADCS] determines and controls the satellite attitude.
+\item Auxiliary Electronics [AUX] subsystems control the deploying mechanisms and monitor the
+solar arrays. The Aux subsystem also contains the rigid backplane of the satellite; therefore, it also connects the subsystems.
+\item Structure [STRU]
+\item Ground Support Equipment [EGSE]
+\end{itemize}
+
+\subsection{The detection of GRBs}
+
+The current detector design is a combination of CsI scintillators reaodout by the Multi Pixel Photon Counter (MPPC), which is a kind of the Silicon Photomultiplier device.
+The advantage of this system is a high light output with compact readout area.
+For the localization of GRB, photon statistics is one of important issue.
+Therefore, we need as much light yield as possible.
+Also, since the detector mounting area for the 3U cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$ as described in the beginning of this section, a compact readout device is required.
+Currently, we are evaluating the detector performance using a sample of detector system consist of CsI(Tl) scintillator with a dimension of 150x75x5 mm$^{2}$ readout by Hamamatsu MPPC (latest model: S13360-6050CS with an effective area of 6x6 mm$^{2}$).
+\ref{fig:schem} shows a schematic picture of the location of one side of the detector and actual setup of performance evaluation test.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/scint_on_sate.png}
+\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\end{figure}
+
+It is challenging to readout the scintillation photons for such geometrically large and thin crystal with small readout area because the produced scintillation photons would be suffered by the multiple scattering inside the crystal before reaching the readout area of the MPPC.
+This would degrade the final light yield and affect to the performance of the energy resolution and lower energy threshold.
+In order to overcome this problem, we are planning to apply a multi-channel coincidence readout technique.
+A multi-channel readout increases the readout area and final light yield, simply and improvement of the uniformity of the light yield with respect to the incident gamma-ray position would be expected.
+However, increasing of the readout channel also increase the leakage current, which would be proportional to the readout area.
+The coincidence readout technique would be expected to suppress the effect of the increasing of the leakage current in the resultant spectrum.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/histo_for_det.png}
+\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\end{figure}
+
+Figure 23 shows the latest result of the study of this technique by irradiating 241Am radioisotope.
+Black and red data show the result by the single channel and 2-channel coincidence readout the single channel readout, respectively.
+As one can see obviously, the final light yield corresponding to the 59.5 keV gamma-ray photo absorption peak increases by almost 50 \% for the 2-channel readout.
+By scaling  the 2-channel readout result to the single channel readout for the 59.5 keV peak as shown by the blue curve, we found that the energy resolution improved thanks to the improvement of the uniformity of the position dependence of the light yield.
+Finally, we confirmed that the lower energy threshold for both readout technique achieved to be about 10 keV.
+Further improvement of the uniformity and/or lower energy threshold could be possible by optimizing the install location of the MPPC device.
 
@@
 %http://multimedia.3m.com/mws/media/466120O/esr.pdf
+
+\subsection{The Geant4 platform}
+
+Geant4 \cite{geant1, geant2, geant3} (for GEometry ANd Tracking) is a platform for "the simulation of the passage of particles through matter," using Monte Carlo methods.
+It is the successor of the GEANT series of software toolkits developed by CERN, and the first to use object oriented programming (in C++).
+Its development, maintenance and user support are taken care by the international Geant4 Collaboration.
+Application areas include high energy physics and nuclear experiments, medical, accelerator and space physics studies.
+The software is used by a number of research projects around the world.
+
+The Geant4 software and source code is freely available from the project web site; until version 8.1 (released June 30, 2006), no specific software license for its use existed; Geant4 is now provided under the Geant4 Software License.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/AtlasHalf.jpg}
+\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\end{figure}
+
+Geant4 includes facilities for handling geometry, tracking, detector response, run management, visualization and user interface.
+For many physics simulations, this means less time needs to be spent on the low level details, and researchers can start immediately on the more important aspects of the simulation.
+
+Following is a summary of each of the facilities listed above:
+
+Geometry is an analysis of the physical layout of the experiment, including detectors, absorbers, etc., and considering how this layout will affect the path of particles in the experiment.
+Tracking is simulating the passage of a particle through matter. This involves considering possible interactions and decay processes.
+Detector response is recording when a particle passes through the volume of a detector, and approximating how a real detector would respond.
+Run management is recording the details of each run (a set of events), as well as setting up the experiment in different configurations between runs.
+Geant4 offers a number of options for visualization, including OpenGL, and a familiar user interface, based on Tcsh.
+Geant4 can also perform basic histogramming; it requires external analysis tools or software that implements the AIDA framework for exploiting advanced histogramming features.
+
+Since release 10.0, Geant4 implements multithreading, making use of thread-local storage to allow for efficient generation of simulated events in parallel.
+
+Because of its general purpose nature, Geant4 is well suited for development of computational tools for analysing interactions of particle with matter in many areas. These include:
+
+Space applications where it is used to study interactions between the natural space radiation environment and space hardware or astronauts;
+Medical applications where interactions of radiations used for treatment are simulated.
+Radiation effects in microelectronics where ionizing effects on semiconductor devices are modeled.
+Nuclear physics
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=140.0mm]{images/fluovsnofluo.png}
+\caption{The positions of irradiation for the investigation of the response of the scintillator}
+\end{figure}
+
 \subsubsection{Calibration of the position dependence}
@@
 
+\begin{figure}[htbp]
+ \centering % \begin{center}/\end{center} takes some additional vertical space
+ \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_600km_AE-8_MIN_averaged_spectra.png}
+ \qquad
+ \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AE-8_MAX_averaged_spectra.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \end{figure}
+
 Protons
@@
 %'DFlux','cm^-2 s^-1 MeV^-1','Differential Flux'
+
+\begin{figure}[htbp]
+ \centering % \begin{center}/\end{center} takes some additional vertical space
+ \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_600km_AP-8_MIN_averaged_spectra.png}
+ \qquad
+ \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AP-8_MAX_averaged_spectra.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \end{figure}
 
@@
 
+Gabor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations.
+András Pál made vital comments on the description of the electronics.
+Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.
+
 \pagebreak
@@
 
-\bibitem{tgemadv} C. Shalem, R. Chechik, et al.,\\
-Advances in Thick GEM-like gaseous electron multipliers—Part I: atmospheric pressure operation,\\
-Nuclear Instruments and Methods in Physics Research A, vol. 558, page 475-489, 2006
+\bibitem{grb1} Mészáros P., 2006, Reports on Progress in Physics, 69, 2259
+%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf
+
+\bibitem{grb2} Vedrenne G., \& Atteia J.-L., 2009, Gamma-Ray Bursts: The brightest explosions in the Universe,
+Springer Praxis Books in Astronomy and Planetary Sciences, Published in association with Praxis
+Publishing, UK
+%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf
+
+\bibitem{grb3} Kouveliotou C., Wijers R. A. M. J., \& Woosley S., 2012, Gamma-ray Bursts, Cambridge, UK:
+Cambridge University Press
+%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf
+
+\bibitem{grb4} Gehrels N., \& Mészáros P. 2012, Science, 337, 932
+%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf
+
+\bibitem{grb5} Klebesadel R. W., Strong I. B., \& Olson R. A. 1973, The Astrophysical Journal, 182, L85
+
+\bibitem{grb6} Kouveliotou C., Meegan C. A., Fishman G. J., et al. 1993, The Astrophysical Journal Letters, 413, L101
+
+\bibitem{grb7} Balázs L. G., Bagoly Z., Horváth I., et al. 2003, Astronomy and Astrophysics, 401, 129
+
+\bibitem{grb8} Mészáros A., Bagoly Z., Balázs L. G., \& Horváth I. 2006, Astronomy and Astrophysics, 455, 785
+
+\bibitem{grb9} Berger E. 2014, Annual Review of Astronomy and Astrophysics, 52, 43
+
+\bibitem{grb10} Rees M. J., \& Meszaros P. 1994, The Astrophysical Journal, 430, L93
+
+\bibitem{grb11} van Paradijs J., Groot P. J., Galama T., et al. 1997, Nature, 386, 686
+
+\bibitem{grb12} Paczynski B. 1986, The Astrophysical Journal, 308, L43
+
+\bibitem{grb13} Woosley S. E., \& Bloom J. S. 2006, Annual Review of Astronomy \& Astrophysics, 44, 507
+
+\bibitem{grb14} Fruchter A. S., Levan A. J., Strolger L., et al. 2006, Nature, 441, 463
+
+\bibitem{grb15} Harrison F. A., Bloom J. S., Frail D. A. et al. 1999, The Astrophysical Journal Letters, 523, L121
+
+\bibitem{grb16} Burrows D. N., Grupe D., Capalbi M., et al. 2006, The Astrophysical Journal, 653, 468
+
+\bibitem{grb17} Abbott B. P., Abbott R., Abbott T. D., et al. 2017, Physical Review Letters, 119, 161101
+
+\bibitem{grb18} Tanvir N. R., Levan A. J., Fruchter A. S., et al. 2013, Nature, 500, 547
+
+\bibitem{grb19} Zhang, B. 2011, Comptes Rendus Physique, 12, 206
+
+\bibitem{grb20} Toma, K., Yoon, S.-C., \& Bromm, V. 2016, Space Science Reviews, 202, 159
+
+\bibitem{grb21} Goldstein A., et al., 2017, The Astrophysical Journal Letters, 848, L14
+
+\bibitem{grb22} Savchenko V., et al., 2017, The Astrophysical Journal Letters, 848, L15
+
+\bibitem{grb23} Troja E., et al., 2017, Naure, 551, 71
+
+\bibitem{grb24} Evans P. A., Cenko S. B., Kennea J. A., et al. 2017, Science, 358, 1565
+
+\bibitem{grb25} Loeb A., 2016, The Astrophysical Journal Letters, 819, L21
+
+\bibitem{grb26} KAGRA Collaboration, Akutsu T., Ando M., et al. 2017, arXiv:1710.04823
+
+\bibitem{grb27} Cavallari E., \& Frontera F. 2017, Space Science Reviews, 212, 429
+
+\bibitem{grb28} Atwood, W. B., \& GLAST Collaboration 1994, Nuclear Instruments and Methods in Physics Research
+A, 342, 302
+
+\bibitem{grb30} Cavallari E., \& Frontera F. 2017, Space Science Reviews, 212, 429
+
+\bibitem{grb31} Barthelmy S. D., Barbier L. M., Cummings J. R., et al. 2005, Space Science Reviews, 120, 143
+
+\bibitem{grb32} Winkler C., Courvoisier T. J.-L., Di Cocco G., et al. 2003, Astronomy and Astrophysics, 411, L1
+
+\bibitem{grb33} Mazets E. P., \& Golenetskii S. V. 1981a, Astrophysics and Space Science, 75, 47
+
+\bibitem{grb34} Tavani M., Barbiellini G., Argan A., et al. 2009, Astronomy and Astrophysics, 502, 995
+
+\bibitem{grb35} Yamaoka K., Yoshida A., Nonaka Y. 2011, 32nd International Cosmic Ray Conference, 9, 111
+
+\bibitem{grb36} Serino M., Sakamoto T., Kawai N., et al. 2014, Publications of the Astronomical Society of Japan, 66,
+87
+
+\bibitem{grb37} Produit N., Barao F., Deluit S., et al. 2005, Nuclear Instruments and Methods in Physics Research A,
+550, 616
+
+\bibitem{grb38} Sadovnichii V. A., Panasyuk M. I., Amelyushkin A. M., et al. 2017, Space Science Reviews, 212, 1705
+
+\bibitem{grb39} Li T., Xiong S., Zhang S., et al. 2018, Science China Physics, Mechanics, and Astronomy, 61, 31011
+
+\bibitem{grb40} Navalgund K. H., Suryanarayana Sarma K., Gaurav P. K., Nagesh G., \& Annadurai M. 2017, Journal of Astrophysics and Astronomy, 38, 34
+
+\bibitem{grb41} Lin R. P., Dennis B. R., Hurford G. J., et al. 2002, Solar Physics, 210, 3
+
+\bibitem{grb42} Hurley K., Mitrofanov I. G., Golovin D., et al. 2013, EAS Publications Series, 61, 459
+
+\bibitem{grb43} Lipunov V., Kornilov V., Gorbovskoy E., et al. 2016, Revista Mexicana de Astronomia y Astrofisica
+Conference Series, 48, 42
+
+\bibitem{grb44} Castro-Tirado A. J., Soldán J., Bernas M., et al. 1999, Astronomy and Astrophysics Supplement, 138, 583
+
+\bibitem{grb45} Akerlof C. W., Kehoe R. L., McKay T. A., et al. 2003, Publications of the Astronomical Society of the Pacific, 115, 132
+
+\bibitem{grb46} Majcher A., Batsch T., Castro-Tirado A. J., et al. 2015, Proceedings of SPIE, 9662, 966219
 
@@
 %https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf
+
+\bibitem{geant1} Nuclear Instruments and Methods in Physics Research A 506 (2003) 250-303
+
+\bibitem{geant2} IEEE Transactions on Nuclear Science 53 No. 1 (2006) 270-278
+
+\bibitem{geant3} Nuclear Instruments and Methods in Physics Research A 835 (2016) 186-225
 

### 2018-05-16 msc_diploma_cubesat_galgoczi.tex
update

@@
  The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.
+
+We are designing a fleet of nanosatellites to perform accurate position determinations
+of short-duration gamma-ray bursts by measuring arrival time differences.
+To achieve sufficient photon statistics to measure the arrival times
+precisely under the severe limitations of size, mass, and power consumption,
+we propose the use of a large-area CsI scintillator that has high light output
+and the use of a small-sized multipixel photon counter (MPPC) that has low
+power consumption. We plan to use one of the latest-model MPPCs provided
+by Hamamatsu Photonics, which has an active area of 6  6 mm2.
+We have compared the performance of two scintillators of different sizes (150 75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards.
+We have found that the two scintillators have similar light yields and each has an energy threshold of $\sim$10 keV at 25C.
+We have also examined the position dependence of the light yield by using radiation from 241Am (59.5 keV) source, and have confirmed that uniformity was improved by using two MPPCs for signal readout.
 
@@
 
-\subsection{The simulated setup}
-
-HAMAMATSU S13360-6050CS
-
-datasheet of QE:
-%http://www.hamamatsu.com/resources/pdf/ssd/s13360_series_kapd1052e.pdf
-
-esr foil:
-Please check "ESR from 3M" company. e.g.,
-%http://multimedia.3m.com/mws/media/466120O/esr.pdf
-
 \subsection{The Geant4 platform}
@@
 
-Space applications where it is used to study interactions between the natural space radiation environment and space hardware or astronauts;
-Medical applications where interactions of radiations used for treatment are simulated.
+Space applications where it is used to study interactions between the natural space radiation environment and space hardware or astronauts; Medical applications where interactions of radiations used for treatment are simulated.
 Radiation effects in microelectronics where ionizing effects on semiconductor devices are modeled.
-Nuclear physics
+
+\subsection{The experimental setup}
+
+We are designing a fleet of nanosatellites to perform accurate position determinations
+of short-duration gamma-ray bursts by measuring arrival time differences.
+To achieve sufficient photon statistics to measure the arrival times
+precisely under the severe limitations of size, mass, and power consumption,
+we propose the use of a large-area CsI scintillator that has high light output
+and the use of a small-sized multipixel photon counter (MPPC) that has low
+power consumption. We plan to use one of the latest-model MPPCs provided
+by Hamamatsu Photonics, which has an active area of 6  6 mm2.
+We have compared the performance of two scintillators of different sizes (150  75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards.
+We have found that the two scintillators have similar light yields and each has an energy threshold of $\sim$10 keV at 25C.
+We have also examined the position dependence of the light yield by using radiation from 241Am (59.5 keV) source, and have confirmed that uniformity was improved by using two MPPCs for signal readout.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/spectracsitl.png}
+\caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/qe.png}
+\caption{The reflectivity $\cite{esr}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/reflectivity.png}
+\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
+\end{figure}
+
+HAMAMATSU S13360-6050CS
+
+ESR foil
+
+QE \cite{qe} of the MPPC
+
+datasheet of QE:
+%http://www.hamamatsu.com/resources/pdf/ssd/s13360_series_kapd1052e.pdf
+
+esr \cite{esr} foil:
+Please check "ESR from 3M" company. e.g.,
+%http://multimedia.3m.com/mws/media/466120O/esr.pdf
 
@@
 
+\pagebreak
+
 \includegraphics[width=130.0mm]{images/2channelelectronics.png}
@@
 
+\pagebreak
+
 \subsection{The satellite}
+
+The direction of GRBs is isotropic in the sky as they are extragalactic objects.
+As the positioning of the scintillators is not decided yet it is important to understand which configuration would be the best for detecting as many GRBs as possible.
+Therefore it is vital to understand how the material of the satellite itself absorbs $\gamma$s.
+The satellite consists of several modules with specific shapes and material contents.
+Therefore building up the whole geometry and material composition was not possible in Geant4, thus the model of the satellite had to be  imported into Geant4.
 
@@
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
  \end{figure}
+
+Importing predefined CAD models into GEANT4 is not always possible or requires intermediate file format conversion to Geometry Description Markup Language (GDML) using commercial or third party software.
+CADMesh \cite{cadmesh} is a direct CAD model import interface for GEANT4 leveraging ASSIMP \cite{assimp} for reading the CAD files.
+In this work the CAD model of the satellite was exported to STL files.
+These files were imported by the CADMesh software to Geant4.
+The tesselation was done by the TETGEN \cite{tetgen} software.
 
@@
 \subsection{Comparison of the results of the simulation with experiments}
+
+\pagebreak
 
@@
 \includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
-\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
+\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
 \end{figure}
@@
  \centering % \begin{center}/\end{center} takes some additional vertical space
- \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_600km_AE-8_MIN_averaged_spectra.png}
+ \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_500km_AE-8_MIN_averaged_spectra.png}
  \qquad
- \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AE-8_MAX_averaged_spectra.png} 
+ \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AE-8_MAX_averaged_spectra.png} 
  % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \caption{\label{fig:band500e} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of electrons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
  \end{figure}
@@
  \centering % \begin{center}/\end{center} takes some additional vertical space
- \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_600km_AP-8_MIN_averaged_spectra.png}
+ \includegraphics[width=.45\textwidth,origin=c,angle=0]{images/alt_500km_AP-8_MIN_averaged_spectra.png}
  \qquad
- \includegraphics[width=.45\textwidth,origin=c]{images/alt_600km_AP-8_MAX_averaged_spectra.png} 
+ \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AP-8_MAX_averaged_spectra.png} 
  % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \caption{\label{fig:band500p} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of protons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
  \end{figure}
@@
 \pagebreak
+
+Put 4 spectra here from the 4 direction to the satellite. Quantify the detected photons by summing up all entries. Where should be the treshold?
+
 \section{Conclusion}
@@
 
+\bibitem{cadmesh} Poole, C. M. and Cornelius, I. and Trapp, J. V. and Langton, C. M., A CAD Interface for GEANT4, Australasian Physical \& Engineering Science in Medicine, 2012
+
+\bibitem{assimp} http://www.assimp.org/
+
+\bibitem{tetgen} Hang Si. 2015. "TetGen, a Delaunay-Based Quality Tetrahedral Mesh Generator". ACM Trans. on Mathematical Software. 41 (2), Article 11 (February 2015), 36 pages
+
+\bibitem{scinti} http://www.amcrys.com/pdf/4279\_.pdf
+
+\bibitem{qe} http://www.hamamatsu.com/resources/pdf/ssd/s13360\_series\_kapd1052e.pdf
+
+\bibitem{esr} http://multimedia.3m.com/mws/media/466120O/esr.pdf
+
 \end{thebibliography}

### 2018-05-19 msc_diploma_cubesat_galgoczi.tex
aa
update

@@
 
-High energy astrophysics
-
-The main aim of the paper, therefore this thesis is to optimize the scintillators of the CubeSats (miniaturized satellites) in the Constellation Gamma satellites.
-It is not known which would be the best detector configuration for the detection of GRBs.
-In the
-
- The second aim is to understand how the material of the CubeSat would affect the gamma photons that the satellite is meant to detect.
+The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs with the Constellation Gamma (Camelot)  CubeSats (miniaturized satellites).
+The Geant4 simulation described in this paper also predicts the background signal originating from solar and cosmic protons and electrons.
+
+First the parameters of the simulation had to be fine tuned to reproduce the measured spectra in the laboratory.
+The simulation of the number of optical photons being deteted was sufficent to predict the signal as the electronic amplification is linear.
+
+The build up of the satellite is quite complex, consisiting of 9 modules, each with a specific material composition.
+Therefore the CAD model of the satellite was imported into Geant4 in order to understand how the satellite itself would affect the measurements.
+The "calibrated" scintillator afterwards was placed on the side of the satellite.
+
+Three cases were investigated.
+First, the model of the detector and the satellite was radiated with a parallel gamma beam that had the same parameters as GRB 9900123, the reference GRB chosen.
+The position of the source was rotated spherically around the satellite.
+In this way the absorbtion of $\gamma$s in the material of the satellite was investigated.
+
+Secondly the cosmic background induced by the protons and electrons was simulated.
+The energy spectrum of electrons and protons was obatined from the SPENVIS information system.
+The satellite was radiated with these given energy distributions and fluxes.
 
@@
 
+ \pagebreak
+
 \subsection{Gamma-ray bursts}
 
-Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} have been studied already about four decades, nonetheless their origin is still not fully understood.
-They are one of the most extreme explosive events ever observed.
-In spite of tremendous effort and numerous observations there are still open questions concerning their detailed physics.
-GRBs were discovered in years 1967–73 by military Vela satellites and later reported to the scientific community in early seventies \cite{grb5}.
-They occur roughly once per day and are characterized by flashes of $\gamma$-rays typically lasting from a fraction of a second to thousands of seconds, typically in the energy range from several keV to several MeV, however $\gamma$-rays of energy >1 GeV associated with GRBs were detected as well.
-A GRB event outshines any other gamma-ray source on the sky.
-It has been found that the duration distribution of their $\gamma$-ray prompt emission is bimodial \cite{grb6} which suggested that there were two groups of GRBs.
-Later, based on more observations, it has been confirmed that these two GRB groups were two distinct astrophysical populations \cite{grb6,grb7,grb8}: I.
-so called long GRBs (LGRBs) with softer spectrum and with prompt $\gamma$-ray emission $\geqslant$2 s that were identified to be gravitational collapses of massive stars due to their association with type Ic core-collapse supernovae, and II.
-so called short GRBs (SGRBs) with harder spectrum and with prompt $\gamma$-ray emission $\leqslant$2 s originating in merger of two compact objects such as neutron star - neutron star (NS-NS) or neutron star - black hole (NS-BH) \cite{grb9}.
+Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} are one of the most invesitaged and yet less understood astrophysical objects.
+The have been studied for more than fourty years as one of the most extreme explosive events in the Universe.
+Their origin is still not yet fully understood.
+GRBs were discovered in years 1967–73 by military satellites.
+The scientific community only got to know their existance in the early seventies \cite{grb5}.
+A GRB event is brighter than any other object in the sky during their appearance that can last from millisecond to minutes.
+Every day the a new GRB is observed by the satellites investigating them.
+The main part of the energy spectrum of these events is from the keV to the MeV ranges.
+
+After a decade of investigation it was found that these events can be categorized into two groups by their length \cite{grb6,grb7,grb8}.
+The first group is called long GRBs with softer spectrum and with prompt $\gamma$-ray emission of $\geqslant$2 s.
+These GRBs were linked to the gravitational collapses of massive stars.
+These objects are associated  with type Ic core-collapse supernovae.
+The second group of GRBs are called short GRBs as their prompt $\gamma$-ray emission lasts $\leqslant$2 s.
+These objects also pocess a harder spectrum.
+They were linked to the merge of two very compact objects, such as neutron star - neutron star (NS-NS) and neutron star - black hole (NS-BH) mergers \cite{grb9}.
 
@@
 
-It was proposed that GRBs were created in collisions of highly relativistic outflow of the accelerated jetted matter \cite{grb10}.
-In many cases it was found that the prompt $\gamma$-ray emission is followed by longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11} explained as a result of the propagation of a relativistic shockwave through the circumburst medium.
-The suggestion that GRBs lie at cosmological distances \cite{grb12} was confirmed by numerous observations and it was found that their redshifts are up to z=9.4 with $\langle$ z $\rangle\approx$0.5 for SGRBs and $\langle$z$\rangle \approx$2.0 for LGRBs [18].
-The energy content 51 released in a GRB is $\sim$10 erg.
-In some cases of LGRBs there was observed supernova component in the lightcurve or in the spectrum of its afterglow, peaking $\sim$2 weeks after the initial trigger \cite{grb13}.
-LGRBs are associated with the brightest regions of galaxies and with the most massive stars \cite{grb14}.
-The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5].
+One of the most accepted theories describe GRBs as collisions of highly relativistic outflow of the accelerated jetted matter \cite{grb10}.
+For most of the observed GRBs the prompt $\gamma$-ray emission was followed by longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11}.
+This is due to the propagation of a relativistic shockwave through the medium that surrounds the burst.
+Obsrvations proved that GRBs are at cosmological distances \cite{grb12}.
+The farthest GRB observed was at a distance of z=9.4.
+The avarge short GRBs lie at a distance of z=0.5.
+The long GRBs are even farther away, on avarage at z=2.
+The energy that is released is tremendous, about 10 erg.
+Long GRBs have been linked to the brightest regions of galaxies that contains the the most massive stars \cite{grb14}.
+%The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5].
 The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 \cite{grb15}.
@@
 
-Observations suggest that SGRBs arise from old astrophysical populations.
-The beaming angles for SGRBs jets seems to be from $\sim$5 to > 25 \cite{grb16}.
-The model that they originate in the merger of two NS has been recently confirmed by the detection of the gravitational wave (GW) signal by LIGO / Virgo collaboration 1, 2.
-This GW signal was accompanied with a SGRB detected by the Fermi /Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}.
-In case of SGRBs a kilonova/macronova can be observed.
-It emits electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.
+On the contrary, short GRBs are thought to originate in old populations.
+The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves of such an event.
+This was detected by the LIGO/Virgo collaboration in 2017 \cite{gravwave}.
+The electromagnetic counterpart of this gravitational wave event was detected as a short GRB by the Fermi/Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}.
+Short GRBs emit electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.
 
@@
 \caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\label{fig:grb_band}
 \end{figure}
@@
 
-In spite of great theoretical and observational successes over the last four decades, many key questions remain about the physics of GRBs.
-For a detailed review see \cite{grb19}.
-Some of these key questions are following.
-
-Central engine: it is usually considered that as a result of the core collapse of a massive star or as a result of a merger of two compact objects there is a newborn BH created.
-Some models also consider that instead of a BH, a rapidly rotating NS with strong surface magnetic field (magnetar), B$\geqslant	$10$^{11}$ T, is formed.
-Another suggested possibility is a formation of a never observationally confirmed quark star composed of quark matter.
-The particle acceleration mechanism in the relativistic shocks and the microphysics of the shocks is a major open issue in the GRB physics. 
-GRB jet composition: it is still debated if the GRB outflow is baryonic or magnetic field (Poynting flux) dominated.
-The jet composition is tied to whether GRBs can accelerate protons to ultra-high energies and produce Ultra-High Energy Cosmic Rays (UHECRs) and high energy neutrinos.
-The models which expect GRBs to be sources of UHECR and high energy neutrinos invoke a baryon-dominated outflow.
-Radiation mechanism: the prompt emission of GRBs is non-thermal, smoothly-joint broken-power-law called “Band” function.
-The emission is required to be produced by a population of particles, e.g.
-leptons, with a power law distribution of their energies.
-The main assumed mechanisms are synchrotron radiation, Synchrotron Self-Compton radiation, and Compton up-scattering of thermal photons however it is difficult to identify the correct radiation mechanism with the current available
-data.
-First stars (Pop III): what is the expected signature of GRBs originating in the death of the first metal-free massive stars at high redshift?
-It was estimated that the mass of the BH at the center of the collapsar of Pop III star is a factor of ten larger and Pop III GRBs may thus tend to have larger durations than those of ordinary Pop I and Pop II GRBs \cite{grb20}.
-Classification: there are cases of GRBs which do not exactly fit in the usual short/long classification.
-For example the ultra-long GRBs or short GRBs with soft extended emission. Next question is what is
-the nature of the precursors in some of the GRB light curves?
-Recent detection of the electromagnetic (EM) signal of the short GRB 170817A \cite{grb21} associated with a GW signal GW170817 produced by a binary neutron star (BNS) merger \cite{grb17} marks a milestone in the multi-messenger research of GRBs and means a great importance of the efforts of searching for EM counterparts to GW sources with spaceborn instruments.
+Despite the fact that GRBs have been studied for more than fourty years a lot of questions are still not understood about their physics\cite{grb19}.
+In the following the main open questions are listed:
+
+\begin{itemize}
+\item{Classification: some of the observed light curves can not be classified into short and long GRBs, such as the ultra-long GRBs.}
+\item{Central engine: in most cases it is thought that a black hole is formed after the merging of neutron stars and core collapse of massive starts.
+Although there are models that predict the birth of a magnetar.
+The most exotic theories predict the birth of a quark star that has never yet been observed.}
+\item{Acceleration mechanism of the jets: How particles are accelerated to a velocity of Lorentz-factor of 300 in the shock waves is not yet understood.}
+\item{GRB jet composition: there are two possible driving forces behind the acceleration of jet material.
+The first one is magnetic field dominated and the other one is dominated by baryons.
+As the acceleration of particles is not yet fully understood, it is not known whether protons can be accelerated to ultra-high energies.
+These could produce Ultra-High Energy Cosmic Rays.}
+\item{Radiation mechanism: there are several physical processes that create the $\gamma$-ray spectrum of GRBs, that is called  the "Band" function.
+The following three processes are though to be the main contributors to the spectrum: synchrotron radiation, synchrotron self-compton radiation and Compton up-scattering of thermal photons.}
+\item{First stars: different population of stars on avarage have different masses.
+Models predit that population III stars end their life with a black hole that has a mass about ten times bigger than population I and II stars.
+The progenitors of GRBs can be classified into populations by their redshift \cite{grb20}.}
+
+\end{itemize}
+
+\subsection{Search for the electromagnetic counterparts of gravitational wave events}
+
+Multi-messenger astronomy is based on the investigation of astronomical objects with disparate "messengers".
+It opened a possibility gather information in different ways to understand astrophysical objects.
+Until 2017 the three messenger were electromagnetic radiation, cosmic rays and neutrinos.
+2017 opened a new era in multi-messenger astronomy as the electromagnetic counterpart of GW signal GW170817 was detected by the LIGO/Virgo collaboration.
+The source of this signal was the short GRB 170817A \cite{grb21}, a binary neutron star merger \cite{grb17} marks.
+
 The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A.
@@
 \includegraphics[width=130.0mm]{images/fovvsloc.png}
-\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\caption{The field of view and localization accuracy of several missions}
 \end{figure}
@@
 \includegraphics[width=130.0mm]{images/satellite_modules.png}
-\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\caption{The modules of the satellite}
 \end{figure}
@@
 \includegraphics[width=130.0mm]{images/scint_on_sate.png}
-\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\caption{Side extensions including of the CAMELOT satellite (left) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right)}
 \end{figure}
@@
 \includegraphics[width=130.0mm]{images/histo_for_det.png}
-\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\label{fig:spectras_meas}
+\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out}
 \end{figure}
@@
 \includegraphics[width=130.0mm]{images/AtlasHalf.jpg}
-\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\caption{The Geant4 simulation of the whole ATLAS experiment}
 \end{figure}
@@
 \includegraphics[width=130.0mm]{images/spectracsitl.png}
+\caption{The emitted scintillation light spectra of three types of scintillators. In our experiment CsI(Tl) was used}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/qe.png}
+\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/reflectivity.png}
 \caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=130.0mm]{images/qe.png}
-\caption{The reflectivity $\cite{esr}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=130.0mm]{images/reflectivity.png}
-\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
 \end{figure}
@@
 \section{Setup}
+
+We obtained energy spectra by using two radioisotopes (109Cd and 241Am) to evaluate the performance of our CsI scintillator + MPPC system.
+We placed a CsI scintillator and an MPPC in an aluminum case (2 mm thick) installed in the thermostatically controlled chamber (ESPEC LU-113).
+We set the operating temperature to 25C.
+We first tested a one-MPPC readout by using a commercial charge-sensitive preamplifier (CLEAR-PULSE 5028), a shaping amplifier (EG\&G ORTEC 571), and an ADC (AMPTEC MCA800A).
+We set the shaping time to 1 $\mu$s.
+We then tested a two-MPPC readout by using an 3 FADC Board (SHIMAFUJI Electric) originally developed for an astrophysical polarimetry mission PoGO+ [9] in order to read and sum the signals of coincident events; the shaping time for this test was set at 2.2 $\mu$s.
+Figure 1 shows the setup of the experiment.
+We installed two lead sheets (identical in size to the scintillator) to collimate signals from the radioisotopes(3.3).
+We tested two CsI scintillators obtained from Amcrys with different sizes (150  75  5 mm3 and 100  75  5 mm3).
+Each was covered with one layer of ESR as a reflector.
+We used one of the latest-model MPPCs by Hamamatsu Photonics, namely, S13360-6050CS, which has an active area of 6  6 mm2 [10].
+We attached an MPPC to the center of the narrower side plane of the scintillator (with an area of 75  5 mm3) for the one-MPPC readout.
+For the two-MPPC readout, we attached the MPPCs 18.75 mm from the edge of the plane.
+The breakdown voltages of the two-MPPCs are almost the same–50.82 and 50.87 V–at 25 C.
+We used a KEITHLEY 2400 to supply the operational voltage of 53.4 V.
+In analyzing of the obtained data, we evaluated four items:
+the light yields of the two scintillators, the energy thresholds, the
+uniformity of the light yield, and the energy resolution.
 
@@
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:i} The scintillator on the left and the box holding the setup on the right}
+ \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right}
  \end{figure}
@@
 \includegraphics[width=130.0mm]{images/1channelelectronics.png}
+\caption{The schematic design of the readout of the MPPC for the 1 channel configuration}
+\label{fig:el1ch}
 \end{figure}
@@
 
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c|c|c|c|} 
+ \hline
+ Energy [eV] & 3.54 & 3.10 & 2.76*eV & 2.48*eV & 2.36*eV & 2.25*eV & 2.07*eV & 1.91*eV\\\hline
+ Relative emittance & 0.02 & 0.1 & 0.3 & 0.6 & 0.9 & 1.0 & 0.7 & 0.4 \\\hline
+ Refractive index & 1.59 & 1.57 & 1.54 & 1.54 & 1.54 & 1.54 & 1.54 & 1.54 \\\hline
+ Absorption lengh [cm] & 50 & 50 & 50 & 50 & 50 & 50 & 50 & 50  \\\hline
+
+ \hline
+\end{tabular}
+\end{center}
+\caption{The mass ratio of materials that are used for the satellite}
+\end{table}
+
+%  CsI_mt->AddConstProperty("RESOLUTIONSCALE",1.0);
+%  CsI_mt->AddConstProperty("SLOWTIMECONSTANT",200.*ns);
+%  CsI_mt->AddConstProperty("YIELDRATIO",1.0);
+
+% G4double glass_RIND[lxenum]={1.49,1.49,1.49};
+%  G4double glass_AbsLength[lxenum]={420.*cm,420.*cm,420.*cm};  
+%  G4double reflectivity[num] = {0.995, 0.995};
+%G4double photocath_EFF[num]={1.,1.}; //Enables 'detection' of photons
+%  G4double photocath_ReR[num]={1.92,1.92};
+%  G4double photocath_ImR[num]={1.69,1.69};
+
 \begin{itemize}
-\item Scintillation yield (Number of photons produced by given keV depleted in the scintillator)
-\item The energy spectra of the produced scintillation
-\item The time constant of the scintillation photon creation
-\item The absorbtion length of the optical photons
-\item Birks constant?
+\item Scintillation yield (Number of photons produced by given keV depleted in the scintillator): 540 1/keV
+\item The time constant of the scintillation photon creation: 200 ns (exponential decay)
 \end{itemize}
@@
 
+\begin{figure}
 \includegraphics[width=150.0mm]{images/irradiation.png}
+\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
+\end{figure}
 
@@
 
-\subsection{Fine tuning the optical parameters}
-
-Most relevant parameters:
-\begin{itemize}
-\item absoprtion length of the scintillator material
-\item reflection of the ESR (Enchanced Specular Reflector) tape the is wrapped around the scintillator 
-\item scintillation yield
-\end{itemize}
-
 \pagebreak
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
@@
 
-\pagebreak
-
+\begin{figure}[h!]
+\centering
 \includegraphics[width=130.0mm]{images/2channelelectronics.png}
-
-\begin{figure}[H]
+\caption{The schematic design of the readout electronics of the 2 channel setup}
+\end{figure}
+
+\begin{figure}[h!]
 \centering
@@
 Only the photons that were detected are drawn.}
+\label{fig:sim_setup}
 \end{figure}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
  \centering % \begin{center}/\end{center} takes some additional vertical space
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \includegraphics[width=150.0mm]{images/satellite_rad.png}
@@
 
-\begin{table}
+\begin{table}[h!]
 \begin{center}
@@
 
-\begin{table}
-
+\begin{table}[h!]
 \begin{center}
@@
 
-Histogram without fluorescence, turned out in LXeEMPhysics line 140-159
-
-Histogram with flo
-
-\begin{figure}
+The measured spectra of the scintillation light created by $\gamma$-rays (fig.
+\ref{fig:spectras_meas}) has a main peak that corresponds to the 60 keV $\gamma$s from the $^{241}$Am source.
+There is an additional peak with an amplitude of roughly 20 \% of the main peak.
+The physical process that is behind this is the X-ray fluoresence.
+By default this process is not included in the Geant4 simulations, thus I had to turn it on.
+A histogram with and without x-ray fluorescence can be seen in fig.
+\ref{fig:fluo}
+
+\begin{figure}[h!]
 \centering
 \includegraphics[width=140.0mm]{images/fluovsnofluo.png}
-\caption{The positions of irradiation for the investigation of the response of the scintillator}
-\end{figure}
+\caption{The obtained energy spectra from simulation with and without x-ray fluoresence being turned on.
+One can see that, the first peak, which can be seen in the experiments only appear when x-ray fluorescence was turned on.}
+\label{fig:fluo}
+\end{figure}
+
+\pagebreak
 
@@
 
-%ADC / energy calibration from measurement 20170829 illetve az egy chanellel: grb\_status3
-
-1 channel read out:
-
-\begin{figure}
+The main aim of this thesis is to predict what signal the satellite would measure in space.
+In order to fine tune the parameters of the simulation experimental data was used.
+The light yield from different parts of the detector is different as scintillation photons have to travel a different distance and they need to be reflected back from the ESR tape that is wrapped around the detector.
+
+\begin{figure}[h!]
 \centering
@@
 
-The experimental results:
-
+A lead sheet was drilled with nine holes to collimate the $\gamma$ source to certain parts of the scintillator.
+These measurements were carried out by Kento Torigoe at the University of Hiroshima.
+This configuration with a lead sheet was built up in Geant4 (fig.
+\ref{fig:sim_setup} and 3.6 million $\gamma$s were simulated at each position.
+
+\begin{table}[h!]
 \begin{center}
@@
 \end{tabular}
+\label{tab:exp_sim}
+\caption{The position dependence of the photon yield measured at the Univeristy of Hiroshima by Kento Torigoe}
 \end{center}
-
-The parameters set in the simulation: reflectivity: 0.995 and absoprtion length of
-40 cm:
-
+\end{table}
+
+The three most relevant parameters of the setup in this case are the scintillation photon yield of the scintillator, the reflection rate of the ESR tape and the self-absorption of the scintillator.
+The photon yield was fixed to 540 $keV^{-1}$ taken from the data sheet of the scintillator \cite{scinti}.
+The self-absorption and the reflection rate was increased until the position dependence was the same as in the experiment (table.
+\ref{tabl:simulated}).
+
+%ADC / energy calibration from measurement 20170829 illetve az egy chanellel: grb\_status3
+
+\begin{table}[h!]
 \begin{center}
@@
 \hline
-  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
-  Pos. of main peak & 0.3389 & 0.3256 & 0.3355 & 0.3521 & 0.3555 & 0.3522 & 0.2060 & 1 & 0.203  \\ 
- \hline
-\end{tabular}
-\end{center}
-
-The parameters set in the simulation: reflectivity: 0.995 and absoprtion length of 50 cm
-
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
+Refl:& 0.995 & Abs.:& 50 cm   &  &  &  &  &  &  \\ 
 \hline
@@
  \hline   
-\end{tabular}
-\end{center}
-
-Reflectivity of 0.997 and abs. length of 60 cm
-
-\begin{center}
-\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
+\hline
+ Refl:& 0.997 & Abs.:& 60 cm   &  &  &  &  &  &  \\ 
  \hline
@@
   Pos. of main peak & 0.4588 & 0.4587 & 0.4697 & 0.4734 & 0.4700 & 0.4737 & 0.3388 & 1 & 0.3365  \\ 
+ \hline \hline
+Refl:& 0.999 & Abs.:& 80 cm   &  &  &  &  &  &  \\ 
+ \hline
+  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+  Pos. of main peak &  &  &  &  &  &  &  & 1 &   \\ 
+ \hline \hline
+Refl:& 0.9996 & Abs.:& 80 cm   &  &  &  &  &  &  \\ 
+ \hline
+  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+  Pos. of main peak &  &  &  &  &  &  &  & 1 &  \\ 
   \hline
 \end{tabular}
+ \caption{The position of the Gaussian peak fitted to the 60 keV peak of the Am source for several irradiated positions}
+ \label{tabl:simulated}
 \end{center}
-
-\pagebreak
+\end{table}
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
@@
 \subsection{Simulation of the cosmic background in space}
+
+SPENVIS \cite{spenvis}
+
+"SPENVIS is ESA's SPace ENVironment Information System, a WWW interface to models of the space environment and its effects; including cosmic rays, natural radiation belts, solar energetic particles, plasmas, gases, and "micro-particles"."
 
@@
 
+CHange the mass of the payload!
+
+\pagebreak
+
 \section{Conclusion}
 
-In order to simulate how the XXX CubeSat would interact with the cosmic background and how sensitive it would be to the GRBs that it is designed to investigate a Geant4 simulation was built.
+In order to simulate how the Camelot CubeSat would interact with the cosmic background and how sensitive it would be to GRBs that it is designed to investigate a Geant4 simulation was built.
 
@@
 The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs that was used to read out the scintillator.
-
-Secondly, the CAD model of the satellite was exported to Geant4.
-The body of the satellite was divided into 8 modules.
-The chemical components of these modules were included in the simulation.
-The scintillator was placed on the side of the satellite.
-
-Thirdly, the effect of cosmic radiation was invastigated by obtaining the energy spectra of cosmic protons and electrons at the XXX altitude of XXX.
-The satellite was radiated by these particles in Geant4 from all directions to investigate how large the signal of these particles would be.
-This needs to be minimalized as it versenyez with the signal of gamma particles from GRBs.
-
-Finally, the $\gamma$ absorption of the satellite was invastigated.
+After the calibration, the results of the simulation was capable of predicting the signal that would be measured in space.
+
+Secondly, the complex CAD model of the satellite --consisting of 7 modules, each with a give avarage material composition-- was exported to Geant4.
+The scintillator and its read out was placed on the side of the satellite.
+
+Thirdly, the $\gamma$ absorption of the satellite was invastigated.
+Parallel $\gamma$-rays with a flux and energy distribution of GRB 9900123 (fig.
+\ref{fig:grb_band}) was simulated.
+36 positions were investigated by varying the incident angle of the $\gamma$s around the major axis of the satellite.
+
+The results show...
+
+Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic protons and electrons at the altitude of 500km.
+The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123.
+The induced signal of these particles was determined.
+This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
 
@@
 
-Gabor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations.
+Ga\'bor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations.
 András Pál made vital comments on the description of the electronics.
-Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.
+Last but not least the author would like to thank his supervisor, Norbert Werner for the continued contributions to this work.
 
@@
 
-\bibitem{grb13} Woosley S. E., \& Bloom J. S. 2006, Annual Review of Astronomy \& Astrophysics, 44, 507
-
 \bibitem{grb14} Fruchter A. S., Levan A. J., Strolger L., et al. 2006, Nature, 441, 463
 
-\bibitem{grb15} Harrison F. A., Bloom J. S., Frail D. A. et al. 1999, The Astrophysical Journal Letters, 523, L121
-
-\bibitem{grb16} Burrows D. N., Grupe D., Capalbi M., et al. 2006, The Astrophysical Journal, 653, 468
+\bibitem{gravwave} https://arxiv.org/abs/1710.05834
 
@@
 
+\bibitem{spenvis} https://www.spenvis.oma.be/
+
 \end{thebibliography}

### 2018-05-20 msc_diploma_cubesat_galgoczi.tex
aa

@@
 \usepackage[english]{babel}
-
+\usepackage{pdfpages}
 %\usepackage{showkeys}
@@
 \begin{tabular}{ll}
-\centerline{ Témavezetők: } \\
+\centerline{ Témavezető: } \\
 \centerline{ Norbert Werner (ELTE)}
@@
 2017 opened a new era in multi-messenger astronomy as the electromagnetic counterpart of GW signal GW170817 was detected by the LIGO/Virgo collaboration.
-The source of this signal was the short GRB 170817A \cite{grb21}, a binary neutron star merger \cite{grb17} marks.
-
-The discovery was made on August 17, 2017 at 12:41:06 UTC with the Fermi/GBM which detected and triggered on the short gamma-ray burst GRB 170817A.
-Approximately 1.7 prior to this GRB, LIGO-Virgo detector network observed a GW signal GW170817 at 12:41:04.4 UTC which originated from a BNS inspiral.
-The source was localized 9/89within a sky region of 28 deg 2 (90 \% probability), which was the most precisely localized GW signal yet.
-An extensive observing campaign was launched across the electromagnetic spectrum leading to the discovery of a bright optical transient in NGC 4993.
-Observations in $\gamma$-ray, X-ray, and ultraviolet (UV) wavelengths include also INTEGRAL \cite{grb22}, Chandra X-ray Observatory \cite{grb23}, Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR) were performed and a blue kilonova associated with this event was detected \cite{grb24}.
-Some models predict also EM signal from BBH coalescence, for example \cite{grb25}.
-More detections of EM counterpart to GW sources and kilonovae are indeed essential for better understanding of these phenomena and this proposed mission has a great potential to bring new and valuable observational data.
-After the upgrades of LIGO, following the finished observing run O2, there will be O3 run scheduled to start in 2018.
-Further observing runs are expected after next improve of the sensitivity.
-Designed sensitivity is aimed to be achieved in 2021.
-The Kamioka Gravitational Wave Detector (KAGRA) 3 is expected to start the first cryogenic operation in 2018, and the observing runs with a full interferometer are expected in 2020s \cite{grb26}.
-Therefore, more GW detections are expected during the operation of this proposed mission.
+The source of this signal was the short GRB 170817A \cite{grb21}, a binary neutron star merger \cite{grb17}.
+
+This historical detection occured on August 17, 2017.
+The Fermi satellite detected the (short) GRB 170817A, approximately 1.7 s before to the detection of the GRB, LIGO-Virgo detector network observed a GW signal GW170817.
+The origin of this source was a neutron-neutron star merger.
+The source was localized  in a sky region of 28 deg$^{2}$ (with 90 \% confidence).
+
+After the detection of the GRB signal, several space and earth based observatories in a wide range of wavelengths started the investigation of the source.
+The discovery of a bright optical transient linked to the GRB was discovered in NGC 4993.
+Observatories involved in the investigation included Chandra X-ray Observatory \cite{grb23}, INTEGRAL \cite{grb22}, Swift and Nuclear Spectroscopic Telescope ARray (NuSTAR).
+A blue kilonova associated with this event was detected \cite{grb24}.
+It is important to emphasize that not only neutron-neutron star mergers but neutron star-black hole and black hole-black hole mergers can emit electromagnetic signal \cite{grb25}.
+Therefore all short GRBs can be investigated with multi-messenger astronomy in the future.
+As LIGO is constantly upgrading its detectors, gravitational waves will be detected more often.
+An even more sensitive gravitational wave detector is under building callled Kamioka Gravitational Wave Detector (KAGRA).
+First scientific measurements will be taken in the 2020s \cite{grb26}.
 
@@
 
-Various detector types has been used or are planned for space instruments for example gas-filled detectors like proportional counters and Geiger counters; scintillation detectors like inorganic crystal scintillators, e.g.
-NaI(Tl) or CsI(Tl), and plastic scintillators; semiconductor devices like, e.g.
-cryogenically cooled germanium, Cadmium Zinc Telluride (CZT) or Silicon Drift Detector (SDD) technique.
-Other types of detectors used in space missions are Compton scatter telescopes or pair production telescopes.
-Table 3 lists detector technologies capable of detecting GRBs in hard X-ray and gamma-ray range employed in previous and current major instruments.
-For an extensive review of hard X-ray / soft gamma-ray experiments and missions see \cite{grb30}.
+Almost all types of detectors starting from semiconductor based detectors to gas-filled detectors have been used in space.
+In the case of search for GRBs the detection of x-rays is the most relevant.
+Several types of detectors can be used for detecting $\gamma$ photons\cite{grb30}, for example the semiconductor based  German Position Sensitive Proportional Counters (PSPC) of the ROSAT X-ray telescope.
+For our satellite the size of the detector is limited, therefore the best option was the usage of scintillators.
+Mostly used scintillators in space include inorganic crystal scintillators, for example NaI(Tl) or CsI(Tl), and plastic scintillators.
+CsI(Tl) was chosen as the detector of the Camelot CubeSat due to it's high light yield.
 
@@
 
-Several spaceborn instruments and ground-based observatories are currently operating or are planed in
-order to bring more detailed observations of GRBs to better understand their nature. Their overview
-and comparison with the required specification on our proposed mission is given in following
-subsections.
-Our project will benefit from large field of view (FoV) and high localization accuracy. It will provide
-full-sky FoV and due to the advantage of using multiple satellites the occulted area by the Earth will
-be eliminated.
-The expected localization accuracy will be from $\sim$10' to degrees depending on the flux and duration of a GRB.
-This is not achieved by any of the current GRB missions.
-In the current missions either the large FoV or precise localization accuracy is accomplished.
-The large FoV instruments, e.g.
-INTEGRAL/SPI-ACS or Fermi/GBM, have either no localization capability or the localization accuracy is of the order of several degrees.
-On the other hand the current instruments providing localization accuracy of the order of arcmin have limited FoV, e.g.
-Swift/BAT or
-AGILE/Super-AGILE.
-Another advantage of our proposed mission is that the cost is only a fraction of the cost of a big
-satellite missions, e.g. like SVOM, and the concept of multiple cubesats allows higher flexibility in
-terms of extending the fleet by more satellites as well as allows replenishment of failed satellites.
+This subsection provides an overview of the existing missions that are aimed to detect GRBs.
+Field of view (FOV) an localization accuracy are chosen to compare them with the Camelot CubeSat.
+The proposed design of the Camelot satellite has the advantage of a large field of view and a high localization accuray.
+The main idea is that each CubeSat will detect GRBs at the same time.
+By measuring the time difference between the triggering of each satellite, the GRB soure can be triangularized.
+By using more satellites, the field of view will be the full-sky and localization accuracy increases.
+
+The planed localization accuracy is more precise than any other existing GRB mission, that might reach $\sim$10'.
+While providing the highest lcoalization accuray, the field of view would also the be the highest, even larger than the field of view of the INTEGRAL/SPI-ACS and Fermi.
+
+The size and mass of the Camelot CubeSat is less than 1\% of the Fermi telescope.
+Therefore from a fraction of the cost several satellites could be built and deployed in orbit.
+Having several satellites also provide a high redundance.
 
@@
 \includegraphics[width=130.0mm]{images/fovvsloc.png}
-\caption{The field of view and localization accuracy of several missions}
-\end{figure}
-
-Fermi 7 \cite{grb28} was launched in 2008 and the main instruments are the Large Area Telescope (LAT) and the Gamma-ray Burst Monitor. 
-Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 and the main instruments are
-Burst Alert Telescope (BAT), X-ray Telescope (XRT), and UV/Optical Telescope (UVOT).
-INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 \cite{grb32} was launched in
-2002 Among several instruments on board INTEGRAL the ones which detect most of GRBs are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the Imager on Board the Integral Satellite (IBIS).
-Wind/Konus 10 \cite{grb33} was launched in 1994 and its still active GRB instrument is Konus.
-Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 /Super-AGILE \cite{grb34} was launched in
-2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
-CALorimetric Electron Telescope (CALET) 12 \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
-
-Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
-Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of GRB polarization.
-Lomonosov 15 /BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
-The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39}, was launched in 2017.
+\caption{The field of view and localization accuracy of several missions including the Camelot CubeSat.}
+\end{figure}
+
+The following list includes the most relevant, currently ongoing missions looking for GRBs:
+
+\begin{itemize}
+\item Fermi 7 \cite{grb28} was launched in 2008 and its main instruments are Gamma-ray Burst Monitor and the Large Area Telescope (LAT). 
+\item Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 and its main instruments are Burst Alert Telescope (BAT), X-ray Telescope (XRT), and UV/Optical Telescope (UVOT).
+\item INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 \cite{grb32} was launched in 2002.
+The most succesfull instruments on board include are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the "Imager on Board the Integral Satellite (IBIS)" detector.
+\item Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 \cite{grb34} was launched in 2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
+\item CALorimetric Electron Telescope (CALET) 12 \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
+\item Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
+\item Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of GRB polarization.
+\item Lomonosov 15 /BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
+\item The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39}, was launched in 2017.
 It has on board the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
-ASTROSAT 17 \cite{grb40}, was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
-Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 \cite{grb41}, was launched in 2002.
+\item ASTROSAT 17 \cite{grb40}, was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
+\item Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 \cite{grb41}, was launched in 2002.
 It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
-The energy range, FoV and localization accuracy for the instruments of the current missions which observe GRBs is summarized in Table 4.
-Figure 3 shows the FoV vs.
-localization accuracy of the current instruments which detect GRBs.
-For comparison the specification of this project is shown as
-well.
-
-\subsection{Currently operating GRB collection and alert networks}
-
-Our project can potentially contribute to some of the currently operating GRB collection and alertnetworks such as the following ones:
-The InterPlanetary Network (IPN) 27 \cite{grb42} which derives the positions of fast gamma-ray transients of all kinds by triangulation.
+\end{itemize}
+
+%\subsection{Currently operating GRB collection and alert networks}
+
+%Our project can potentially contribute to some of the currently operating GRB collection and alertnetworks such as the following ones:
+%The InterPlanetary Network (IPN) 27 \cite{grb42} which derives the positions of fast gamma-ray transients of all kinds by triangulation.
 Numerous spacecraft and instruments participate in the network at the Earth’s orbit as well as in the interplanetary space.
 It detects about 350/year.
-The Gamma-ray Coordinates Network (Transient Astronomy Network) (GCN/TAN) 28 provides information about GRBs in real-time to the world community.
+%The Gamma-ray Coordinates Network (Transient Astronomy Network) (GCN/TAN) 28 provides information about GRBs in real-time to the world community.
 The network provides the real-time (and near real-time) distribution of GRB locations, images, spectra, and lightcurves detected by various spacecraft and the distribution of follow-up observation reports.
-The Global Relay of Observatories Watching Transients Happen (GROWTH) 29 is an international scientific collaborative project studying the astronomical transients.
-
-\subsection{Current GRB Follow-up observations}
-
-This cubesat project will provide high precision localization accuracy of GRBs allowing efficient follow-up observations by existing ground based observatories.
+%The Global Relay of Observatories Watching Transients Happen (GROWTH) 29 is an international scientific collaborative project studying the astronomical transients.
+
+%\subsection{Current GRB Follow-up observations}
+
+%This cubesat project will provide high precision localization accuracy of GRBs allowing efficient follow-up observations by existing ground based observatories.
 There are several observatories world-wide to perform photometric or spectroscopic observations of GRB afterglows, for example:
-The Mobile Astronomical System of TElescope Robots (MASTER) 30 \cite{grb43} is a global network of robotic telescopes for very fast positioning and follow up of GRBs.
-The Burst Optical Observer and Transient Exploring System (BOOTES) network of robotic telescopes for follow up observations of GRBs.
-31 \cite{grb44} is a world wide The Robotic Optical Transient Search Experiment (ROTSE) 32 [101] are telescopes which operate at
-sites around the world and follow GRBs.
-Pi of the Sky 33 [102] is a system of detectors designed for continuous observation of night sky looking for optical flashes of astrophysical origin, in particular for GRBs.
-Several other telescopes and observatories which provide measurements in optical, infra-red or radio bands are also, e.g.: Gamma-Ray Burst Optical/Near-Infrared Detector (GROND) 34 , the Palomar 60 inch telescope 35 , Rapid Eye Mount (REM) 36 , Livermore Optical Transient Imaging System (Super- LOTIS) 37 , Télescopes à Action Rapide pour les Objets Transitoires (TAROT) 38 , Gran Telescopio Canarias (GTC) 39 , ESO Very Large Telescope (VLT) 40 , Nordic Optical Telescope (NOT) 41 , Observatorio Astronómico Nacional on the Sierra de San Pedro Mártir 42 , Cerro Tololo Inter-American Observatory (CTIO) 43 , Telescopio Nazionale Galileo (TNG) 44 , Gao-Mei-Gu (GMG) station of Yunnan Observatories 45 , Observatorio de Sierra Nevada (OSN) 46 , United Kingdom Infrared Telescope (UKIRT) 47 , Very Large Array (VLA) 48 , Atacama Large Millimeter/Submillimeter Array (ALMA) 49 , James Clerk Maxwell Telescope 50 , Arcminute Microkelvin Imager which robotically triggers on Swift GRBs (AMI-GRB) 51 .
+%The Mobile Astronomical System of TElescope Robots (MASTER) 30 \cite{grb43} is a global network of robotic telescopes for very fast positioning and follow up of GRBs.
+%The Burst Optical Observer and Transient Exploring System (BOOTES) network of robotic telescopes for follow up observations of GRBs.
+31 \cite{grb44} is a world wide The Robotic Optical Transient Search Experiment (ROTSE) 32 [101] are telescopes which operate at sites around the world and follow GRBs.
+%Pi of the Sky 33 [102] is a system of detectors designed for continuous observation of night sky looking for optical flashes of astrophysical origin, in particular for GRBs.
+%Several other telescopes and observatories which provide measurements in optical, infra-red or radio bands are also, e.g.: Gamma-Ray Burst Optical/Near-Infrared Detector (GROND) 34 , the Palomar 60 inch telescope 35 , Rapid Eye Mount (REM) 36 , Livermore Optical Transient Imaging System (Super- LOTIS) 37 , Télescopes à Action Rapide pour les Objets Transitoires (TAROT) 38 , Gran Telescopio Canarias (GTC) 39 , ESO Very Large Telescope (VLT) 40 , Nordic Optical Telescope (NOT) 41 , Observatorio Astronómico Nacional on the Sierra de San Pedro Mártir 42 , Cerro Tololo Inter-American Observatory (CTIO) 43 , Telescopio Nazionale Galileo (TNG) 44 , Gao-Mei-Gu (GMG) station of Yunnan Observatories 45 , Observatorio de Sierra Nevada (OSN) 46 , United Kingdom Infrared Telescope (UKIRT) 47 , Very Large Array (VLA) 48 , Atacama Large Millimeter/Submillimeter Array (ALMA) 49 , James Clerk Maxwell Telescope 50 , Arcminute Microkelvin Imager which robotically triggers on Swift GRBs (AMI-GRB) 51 .
 
@@
 
+The Camelot satellite will consist of the following modules:
+
 \begin{itemize}
-\item The CubeSat platform has the following Sub-systems level elements, Figure 5 shows the sub-systems
-of the CubeSat platform.
 \item On-Board Computer [OBC] is responsible for control all the satellite’s sub-systems. OBC collects housekeeping and payload data and archives them in its internal storage.
@@
 
+\subsection{Simulation of the signal induced by GRBs in the satellite}
+
+One of the key questions is whether
+
 \subsection{Simulation of the cosmic background in space}
@@
 "SPENVIS is ESA's SPace ENVironment Information System, a WWW interface to models of the space environment and its effects; including cosmic rays, natural radiation belts, solar energetic particles, plasmas, gases, and "micro-particles"."
+
+\subsubsection{Proton background}
 
@@
 
+\subsection{Electron background}
+
 Electrons
@@
 
+\subsubsection{$\gamma$ background}
+
 \pagebreak
@@
 
-Ga\'bor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations.
+Gabor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations.
+Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated.
 András Pál made vital comments on the description of the electronics.
-Last but not least the author would like to thank his supervisor, Norbert Werner for the continued contributions to this work.
+Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.
 
@@
 
-\bibitem{grb33} Mazets E. P., \& Golenetskii S. V. 1981a, Astrophysics and Space Science, 75, 47
-
 \bibitem{grb34} Tavani M., Barbiellini G., Argan A., et al. 2009, Astronomy and Astrophysics, 502, 995
@@
 
+\listoffigures
+
+\includepdf[pages=-,pagecommand={},width=\textwidth]{images/nyilatkozat.pdf}
+
 \end{document}

### 2018-05-22 msc_diploma_cubesat_galgoczi.tex
aa

@@
 
+\begin{figure}[h!]
+ \centering % \begin{center}/\end{center} takes some additional vertical space
+ \includegraphics[width=.55\textwidth,origin=c,angle=0]{images/electrons0degspectra.png}
+ \qquad
+ \includegraphics[width=.4\textwidth,origin=c,angle=90]{images/0mac.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ \caption{\label{fig:i} The spectrum measured when the electrons were shot perpendicular to the scintillator (called angle of 0 $^{\circ}$)}
+ \end{figure}
+
+\begin{figure}[h!]
+ \centering % \begin{center}/\end{center} takes some additional vertical space
+ \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
+ \qquad
+ \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/8mac.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
+ \end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=150.0mm]{images/electronabsorption.png}[H!]
+\caption{The ammount of electrons detected from 100.000 shoot in the simulation}
+\end{figure}
+
 \subsubsection{$\gamma$ background}

### 2018-05-22 msc_diploma_cubesat_galgoczi.tex
text

--- 2018-05-20 msc_diploma_cubesat_galgoczi.tex
@@
 
-The current detector design is a combination of CsI scintillators reaodout by the Multi Pixel Photon Counter (MPPC), which is a kind of the Silicon Photomultiplier device.
-The advantage of this system is a high light output with compact readout area.
-For the localization of GRB, photon statistics is one of important issue.
-Therefore, we need as much light yield as possible.
-Also, since the detector mounting area for the 3U cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$ as described in the beginning of this section, a compact readout device is required.
-Currently, we are evaluating the detector performance using a sample of detector system consist of CsI(Tl) scintillator with a dimension of 150x75x5 mm$^{2}$ readout by Hamamatsu MPPC (latest model: S13360-6050CS with an effective area of 6x6 mm$^{2}$).
-\ref{fig:schem} shows a schematic picture of the location of one side of the detector and actual setup of performance evaluation test.
+In the case of our satellite, the detection of $\gamma$ photons from GRBs will be carried out by a Caesium Iodide scintillator doped with Tellurium.
+This is the most popular alkali halide scintillation crystal apart from NaI(Tl).
+The $\gamma$ photons create scintillation, thus thousands of optical photons in the scintillator.
+These photons will be detected by Silicon Photomultiplier device called Multi Pixel Photon Counter, MPPC for short.
+This if by far the best and most compact solution as the size of cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$.
+The first tests were carried out by a single MPPC readout, which was followed by a design with two MPPCs to maximize the light yield and minimalize the noise.
+The size of the Hamamatsu MPPC is 6x6 mm$^{2}$.
+The scintillators will be placed onto the surface of the satellite as can be seen in fig.
+\ref{fig:scints}.
+While fig.
+\ref{fig:schem} shows the experimental setup used for the tests.
 
@@
 \caption{Side extensions including of the CAMELOT satellite (left) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right)}
-\end{figure}
-
-It is challenging to readout the scintillation photons for such geometrically large and thin crystal with small readout area because the produced scintillation photons would be suffered by the multiple scattering inside the crystal before reaching the readout area of the MPPC.
-This would degrade the final light yield and affect to the performance of the energy resolution and lower energy threshold.
-In order to overcome this problem, we are planning to apply a multi-channel coincidence readout technique.
-A multi-channel readout increases the readout area and final light yield, simply and improvement of the uniformity of the light yield with respect to the incident gamma-ray position would be expected.
-However, increasing of the readout channel also increase the leakage current, which would be proportional to the readout area.
-The coincidence readout technique would be expected to suppress the effect of the increasing of the leakage current in the resultant spectrum.
+\label{fig:scints}
+\end{figure}
+
+The large area and small thickness of the scintillator makes it challenging for the read out as optical photons have to be reflected several times to reach the MPPC.
+Two factors play role here, the self absorption of the reflectivity of the tape that is used to cover the scintillator.
+The length of the self absoprtion is in the order of a meter and the reflectivity of the ESR tape, which is above 99 \% can be seen in fig.
+\ref{fig:refl}.
+The idea that we came is using two MPPC-s with coincidence.
+This results in a smaller leakage current (noise) as the noise has a poissonian statistic.
+Therefore the noise is "random" and the chance of a trigger from both of the MPPC has a very low chance.
+The other advantage is the incread photon yield due to the double of the photon collection area.
+The difference between one and two channel readout can be seen in fig.
+\ref{fig:spectra}.
 
@@
 \caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out}
-\end{figure}
-
-Figure 23 shows the latest result of the study of this technique by irradiating 241Am radioisotope.
-Black and red data show the result by the single channel and 2-channel coincidence readout the single channel readout, respectively.
-As one can see obviously, the final light yield corresponding to the 59.5 keV gamma-ray photo absorption peak increases by almost 50 \% for the 2-channel readout.
-By scaling  the 2-channel readout result to the single channel readout for the 59.5 keV peak as shown by the blue curve, we found that the energy resolution improved thanks to the improvement of the uniformity of the position dependence of the light yield.
-Finally, we confirmed that the lower energy threshold for both readout technique achieved to be about 10 keV.
-Further improvement of the uniformity and/or lower energy threshold could be possible by optimizing the install location of the MPPC device.
+\label{fig:spectra}
+\end{figure}
 
@@
 
-Geant4 \cite{geant1, geant2, geant3} (for GEometry ANd Tracking) is a platform for "the simulation of the passage of particles through matter," using Monte Carlo methods.
-It is the successor of the GEANT series of software toolkits developed by CERN, and the first to use object oriented programming (in C++).
+The most used software in particle physics are MCNPX, FLUKA and Geant4.
+For this thesis Geant4 was chosen as it is the best for simulation of several types of particles at the same time and building up the geometry of detectors is most propably is the most convinient in the software.
+
+Geant4 \cite{geant1, geant2, geant3} (for GEometry ANd Tracking) is a platform for "the simulation of the passage of particles through matter," using the Monte Carlo method.
+It has been developed at CERN for more than three decades by dozens of physicst and programmers.
+The cross sections for all interactions between matter and particles are included in this software.
+It is an object orianted programming platform in C++.
 Its development, maintenance and user support are taken care by the international Geant4 Collaboration.
-Application areas include high energy physics and nuclear experiments, medical, accelerator and space physics studies.
-The software is used by a number of research projects around the world.
-
-The Geant4 software and source code is freely available from the project web site; until version 8.1 (released June 30, 2006), no specific software license for its use existed; Geant4 is now provided under the Geant4 Software License.
+Areas in science that has used Geant4 are vary wide from the design of complex medical machines to accelerator, nuclear physics, hight energy physics and space applications.
+Several thousand people use it all around the globe.
 
@@
 
-Geant4 includes facilities for handling geometry, tracking, detector response, run management, visualization and user interface.
-For many physics simulations, this means less time needs to be spent on the low level details, and researchers can start immediately on the more important aspects of the simulation.
-
-Following is a summary of each of the facilities listed above:
-
-Geometry is an analysis of the physical layout of the experiment, including detectors, absorbers, etc., and considering how this layout will affect the path of particles in the experiment.
-Tracking is simulating the passage of a particle through matter. This involves considering possible interactions and decay processes.
-Detector response is recording when a particle passes through the volume of a detector, and approximating how a real detector would respond.
-Run management is recording the details of each run (a set of events), as well as setting up the experiment in different configurations between runs.
-Geant4 offers a number of options for visualization, including OpenGL, and a familiar user interface, based on Tcsh.
-Geant4 can also perform basic histogramming; it requires external analysis tools or software that implements the AIDA framework for exploiting advanced histogramming features.
-
-Since release 10.0, Geant4 implements multithreading, making use of thread-local storage to allow for efficient generation of simulated events in parallel.
-
-Because of its general purpose nature, Geant4 is well suited for development of computational tools for analysing interactions of particle with matter in many areas. These include:
-
-Space applications where it is used to study interactions between the natural space radiation environment and space hardware or astronauts; Medical applications where interactions of radiations used for treatment are simulated.
-Radiation effects in microelectronics where ionizing effects on semiconductor devices are modeled.
+The Geant4 platform includes all the important features required in the full simulation of an experiment from handling the geometry of the detector and readout, tracking of particles in the detectors for visualization.
 
@@
 \caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
+\label{fig:refl}
 \end{figure}
@@
 \caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
+\label{fig:schem}
 \end{figure}
@@
   Pos. of main peak &  &  &  &  &  &  &  & 1 &  \\ 
+  \hline \hline
+Refl:& 0.9999 & Abs.:& 105 cm   &  &  &  &  &  &  \\ 
+ \hline
+  Pos. of source & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ 
+  Pos. of main peak & 0.6911 & 0.6865 & 0.6956 & 0.7002 & 0.6956 & 0.7002 & 0.6041 & 1 & 0.5955 \\ 
   \hline

### 2018-05-23 msc_diploma_cubesat_galgoczi.tex
text

@@
 %kotesre
-\geometry{left=2.5cm,right=1.5cm,top=2.0cm,bottom=2.0cm}
+%\geometry{left=2.5cm,right=1.5cm,top=2.0cm,bottom=2.0cm}
 %standard
-%\geometry{left=2.0cm,right=2.0cm,top=2.0cm,bottom=2.0cm}
+\geometry{left=3.0cm,right=3.0cm,top=2.0cm,bottom=2.0cm}
 
@@
 \includegraphics[width=130.0mm]{images/grb_spectra.png}
-\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
+\caption{The band function of GRB 990123 $\cite{grb_spectra}$}
 \label{fig:grb_band}
@@
 
-We are designing a fleet of nanosatellites to perform accurate position determinations
-of short-duration gamma-ray bursts by measuring arrival time differences.
-To achieve sufficient photon statistics to measure the arrival times
-precisely under the severe limitations of size, mass, and power consumption,
-we propose the use of a large-area CsI scintillator that has high light output
-and the use of a small-sized multipixel photon counter (MPPC) that has low
-power consumption. We plan to use one of the latest-model MPPCs provided
-by Hamamatsu Photonics, which has an active area of 6  6 mm2.
-We have compared the performance of two scintillators of different sizes (150  75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards.
-We have found that the two scintillators have similar light yields and each has an energy threshold of $\sim$10 keV at 25C.
-We have also examined the position dependence of the light yield by using radiation from 241Am (59.5 keV) source, and have confirmed that uniformity was improved by using two MPPCs for signal readout.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=130.0mm]{images/spectracsitl.png}
-\caption{The emitted scintillation light spectra of three types of scintillators. In our experiment CsI(Tl) was used}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=130.0mm]{images/qe.png}
-\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=130.0mm]{images/reflectivity.png}
-\caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
-\label{fig:refl}
-\end{figure}
-
-HAMAMATSU S13360-6050CS
-
-ESR foil
-
-QE \cite{qe} of the MPPC
-
-datasheet of QE:
-%http://www.hamamatsu.com/resources/pdf/ssd/s13360_series_kapd1052e.pdf
-
-esr \cite{esr} foil:
-Please check "ESR from 3M" company. e.g.,
-%http://multimedia.3m.com/mws/media/466120O/esr.pdf
-
-\subsection{Simulation}
-
-In order to understand how the $\gamma$ photons -- that the CubeSat is meant to detect -- interact with the matter of the satellite simulations are needed.
-In a simulation it is also possible to determine the optimal geometry that would lead to the best GRB detection.
-
-The Geometry... XXX TRacking (Geant4)
-
-The cross section for photoeffect is far the largest by far for low energy gamma photons.
-The ionized nuclei and the secondary electrons generates scintillation.
-
-\includegraphics[width=130.0mm]{images/secondary.png}
-
-\includegraphics[width=130.0mm]{images/secondary2.png}
-
-Also the nuclei that is ionized by the gamma produces photons.
-
-\section{Setup}
-
-We obtained energy spectra by using two radioisotopes (109Cd and 241Am) to evaluate the performance of our CsI scintillator + MPPC system.
-We placed a CsI scintillator and an MPPC in an aluminum case (2 mm thick) installed in the thermostatically controlled chamber (ESPEC LU-113).
-We set the operating temperature to 25C.
-We first tested a one-MPPC readout by using a commercial charge-sensitive preamplifier (CLEAR-PULSE 5028), a shaping amplifier (EG\&G ORTEC 571), and an ADC (AMPTEC MCA800A).
-We set the shaping time to 1 $\mu$s.
-We then tested a two-MPPC readout by using an 3 FADC Board (SHIMAFUJI Electric) originally developed for an astrophysical polarimetry mission PoGO+ [9] in order to read and sum the signals of coincident events; the shaping time for this test was set at 2.2 $\mu$s.
-Figure 1 shows the setup of the experiment.
-We installed two lead sheets (identical in size to the scintillator) to collimate signals from the radioisotopes(3.3).
-We tested two CsI scintillators obtained from Amcrys with different sizes (150  75  5 mm3 and 100  75  5 mm3).
-Each was covered with one layer of ESR as a reflector.
-We used one of the latest-model MPPCs by Hamamatsu Photonics, namely, S13360-6050CS, which has an active area of 6  6 mm2 [10].
-We attached an MPPC to the center of the narrower side plane of the scintillator (with an area of 75  5 mm3) for the one-MPPC readout.
-For the two-MPPC readout, we attached the MPPCs 18.75 mm from the edge of the plane.
-The breakdown voltages of the two-MPPCs are almost the same–50.82 and 50.87 V–at 25 C.
-We used a KEITHLEY 2400 to supply the operational voltage of 53.4 V.
-In analyzing of the obtained data, we evaluated four items:
-the light yields of the two scintillators, the energy thresholds, the
-uniformity of the light yield, and the energy resolution.
+In order to understand and charaterize the behaviour of the large-area CsI(Tl) scintillator detector and the MPPC readout an experimental setup was built in Hiroshima, Japan.
+The experimental setup provided vital information for the simulation, mostly for the position dependence of the light yield.
+Different $\gamma$ source were used, mostly an $^{241}$Am source.
 
@@
 
-\begin{figure}
-\includegraphics[width=130.0mm]{images/1channelelectronics.png}
-\caption{The schematic design of the readout of the MPPC for the 1 channel configuration}
-\label{fig:el1ch}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=130.0mm]{images/tap1channel.png}
-\caption{\label{fig:1channeltape} The MPPC is fixed to the scintillator with valqua tape}
-\end{figure}
-
-Size of the scintillator is, the aluminium housing thickness is, the size of the SiPM is...
-
-Parameters of the CsI(Tl) scintillator REF
+The detector was wrapped in a so called ESR foil that is designed to reflect as much light as possible.
+In fig.
+\ref{fig:refl} the reflectivity of this tape can be seen depending on the wavelenght of the photons, exceeding 99 \% for most of the wavelengths.
+It is important as the optical photons have to be reflected several times in order to be read out with the small effective are of the MPPC.
+This reflectivity was included in the simulation.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/reflectivity.png}
+\caption{The reflectivity $\cite{scinti}$ of the ESR tape that was used to wrap the scintillator in order to increase the light yield. This data was included in the simulation.}
+\label{fig:refl}
+\end{figure}
+
+The CsI(Tl) scintillator used is produced by AmCrys \cite{scinti}.
+The dimension of this detector are 150 mm x 75 mm x 5 mm, the largest possible size that can fit onto the surface of the detector.
+The spectra of the optical photons produced in the scintillation process can be seen in fig.
+\ref{fig:scint_yield}.
+An aluminium case of 2mm is used, the same as planned for the mission in space.
+The time constant for the scintillation of the detector was 200 ns.
 
@@
  \hline
- Energy [eV] & 3.54 & 3.10 & 2.76*eV & 2.48*eV & 2.36*eV & 2.25*eV & 2.07*eV & 1.91*eV\\\hline
+ Energy [eV] & 3.54 & 3.10 & 2.76 & 2.48 & 2.36 & 2.25 & 2.07 & 1.91\\\hline
  Relative emittance & 0.02 & 0.1 & 0.3 & 0.6 & 0.9 & 1.0 & 0.7 & 0.4 \\\hline
@@
  Absorption lengh [cm] & 50 & 50 & 50 & 50 & 50 & 50 & 50 & 50  \\\hline
-
- \hline
 \end{tabular}
 \end{center}
-\caption{The mass ratio of materials that are used for the satellite}
+\caption{The parameters of the CsI(Tl) scintillator used in our experiment}
 \end{table}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/spectracsitl.png}
+\caption{The emitted scintillation light spectra of three types of scintillators. In our experiment CsI(Tl) was used}
+\label{fig:scint_yield}
+\end{figure}
+
+The MPPC chosen for this satellite is one of the latest models (HAMAMATSU S13360-6050CS) \cite{qe}.
+It has an effective area of 6mm x 6mm.
+The photon detection efficiency of this specific model can be seen in fig.
+\ref{fig:qe}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=130.0mm]{images/qe.png}
+\caption{The photon detection efficiency $\cite{qe}$ of the MPPCs used for the readout of the scintillators. This data was included in the simulation.}
+\label{fig:qe}
+\end{figure}
+
+\subsection{The readout of the detector}
+
+The response of the MPPC detector used depends on temperature.
+Therefore the experimental setup was placed in a thermostatically controlled chamber (ESPEC LU-113) keeping the temperature at 25$^{\circ}$.
+Two setups were investigated.
+The first one with a single MPPC readout placed in the middle of one side of the scintillator.
+In the other case two MPPCs were utilized symmetrically placed on one side of the detector.
+
+For the single MPPC readout setup a commercial charge-sensitive preamplifier (CLEAR-PULSE 5028), a shaping amplifier (EG\&G ORTEC 571), and an ADC (AMPTEC MCA800A) were used to obtain an electric signal read out by a PC.
+The shaping times was set to 1 $\mu$s.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=80.0mm]{images/1channelelectronics.png}
+\caption{The schematic design of the readout of the MPPC for the 1 channel configuration}
+\label{fig:el1ch}
+\end{center}
+\end{figure}
+
+For the case of the two-channel read out an FADC board was utilized that contains all the necesarry electronics to read out the signal of the MPPC with an additional coincidence unit.
+This board was developed for the astrophysical polarimetry mission PoGO+.
+The shaping time was set to 2.2 $\mu$s in this case.
+The breakdown voltages of the two-MPPCs are almost the same–50.82 and 50.87 V–at 25 C.
+We used a KEITHLEY 2400 to supply the operational voltage of 53.4 V.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=80.0mm]{images/2channelelectronics.png}
+\caption{The schematic design of the readout electronics of the 2 channel setup}
+\end{figure}
 
@@
 
-\begin{itemize}
-\item Scintillation yield (Number of photons produced by given keV depleted in the scintillator): 540 1/keV
-\item The time constant of the scintillation photon creation: 200 ns (exponential decay)
-\end{itemize}
-
-Optical parameters of the materials and surfaces:
-\begin{itemize}
-\item Refractive indices of all relevant materials
-\item Reflection
-\item The detection efficiency of the SiPM detectors
-\end{itemize}
+\pagebreak
 
 \subsection{1 channel setup}
-
-\begin{figure}
-\includegraphics[width=150.0mm]{images/irradiation.png}
-\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
-\end{figure}
 
@@
 The distance of the source from the scintillator was 13.5 mm.
+
+\begin{figure}[h!]
+\includegraphics[width=150.0mm]{images/irradiation.png}
+\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
+\end{figure}
+
 Therefore the solid angle of the part of the whole sphere where $\gamma$s could be detected was 
@@
 
- Therefore the number of $\gamma$s that hit the scintillator, the Al and Pb sheets above it was:
-$$A = \frac{1.234}{4 \pi} \cdot 471 kBq = 46.25 kBq$$
-
 \pagebreak
@@
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=130.0mm]{images/2channelsetup.png}[H!]
+In order to maximize the light yield, thus the signal of the detector and minimize the noise with coincidence a 2 channel setup was tested.
+In fig.
+\ref{fig:schem2c} this setup can be seen with the MPPCs placed symmetrically to the scintillator.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=130.0mm]{images/2channelsetup.png}
 \caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
-\label{fig:schem}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=130.0mm]{images/2channelelectronics.png}
-\caption{The schematic design of the readout electronics of the 2 channel setup}
-\end{figure}
+\label{fig:schem2c}
+\end{figure}
+
+The geometry of the two channel read out setup was simulated
 
@@
  \centering % \begin{center}/\end{center} takes some additional vertical space
- \includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
+ \includegraphics[width=.35\textwidth,origin=c,angle=0]{images/satellite.png}
  \qquad
@@
 
-\subsection{Simulation of the signal induced by GRBs in the satellite}
-
-One of the key questions is whether
+\subsection{Simulation of the signal induced by GRBs in the satellite} \label{sec:grb}
+
+One of the key questions is what would the satellite measure in space when the $\gamma$ photons of the GRB hit it.
+It is important to understand how the material of the satellite would absorb the $\gamma$ photons.
+
+In order to quantify the detection, the number of particles detected was used as a measure.
+10.000 $\gamma$ particles were shot at the detector paralelly on an area of 60cm x 60cm from several angles around the longitudinal axis of the satellite.
+This way the self absorption of the satellite was quantified.
+
+The energy spectra of $\gamma$ photons (called band function) from GRBs is fitted by the following equation \cite{band_func}:
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=130.0mm]{images/band_function.png}
+\label{eq:bandfunc}
+\end{center}
+\end{figure}
+
+where the parameters of the fit are following for GRB 990123:\\
+$\alpha = -0.87 \pm 0.01 $\\
+$\beta = -2.9 \pm 0.11$\\
+$E_{peak} = (617 \pm 7.09) keV$\\
+$A= (0.0262 \pm 0.0000993) s^{-1}cm^{-1}keV^{-1}$\\
 
@@
 
-SPENVIS \cite{spenvis}
-
-"SPENVIS is ESA's SPace ENVironment Information System, a WWW interface to models of the space environment and its effects; including cosmic rays, natural radiation belts, solar energetic particles, plasmas, gases, and "micro-particles"."
+In order to understand what would give the measured background of the satellites, cosmic and solar protons and electrons were simulated in the same way as the $\gamma$ particles were in sec.
+\ref{sec:grb}.
+The flux of and energy distribution of protons and electrons vary widely in the lower orbits around Earth due to its magnetic field.
+The SPENVIS \cite{spenvis} information system was used to obtain the proton and electron energy spectra.
+
+SPENVIS is ESA's SPace ENVironment Information System, a WWW interface to models of the space environment and its effects; including cosmic rays, natural radiation belts, solar energetic particles, plasmas, gases, and "micro-particles".
 
 \subsubsection{Proton background}
+
+The AE-8 model was used in SPENVIS to obtain the spatially avaraged proton energy spectra for an altitude of 500 km both for solar minimum and maximum.
+The inclination of the orbit was chosen to be 89 $^{\circ}$.
+At the moment hadron resonances are not taken into account in the simulation.
 
@@
 
-Protons
-'Apogee: 500.0 km'
-'Perigee: 500.0 km'
-'Inclination: 89.0 deg'
-
 \subsection{Electron background}
 
-Electrons
-'Trapped electron model: AE-8 MIN'
-%'Energy','MeV','Energy'
-%'IFlux','cm^-2 s^-1','Integral Flux'
-%'DFlux','cm^-2 s^-1 MeV^-1','Differential Flux'
+The AE-8 model was used in SPENVIS to obtain the spatially avaraged elextron energy spectra for an altitude of 500 km both for solar minimum and maximum.
+The inclination of the orbit was chosen to be 89 $^{\circ}$.
+At the moment hadron resonances are not taken into account in the simulation.
 
@@
 
-\subsubsection{$\gamma$ background}
-
-\pagebreak
-
-Put 4 spectra here from the 4 direction to the satellite. Quantify the detected photons by summing up all entries. Where should be the treshold?
-
-CHange the mass of the payload!
-
 \pagebreak
@@
 
+\bibitem{band_func} https://arxiv.org/pdf/1311.7135.pdf
+
 \bibitem{spenvis} https://www.spenvis.oma.be/

### 2018-05-24 msc_diploma_cubesat_galgoczi.tex
aa

@@
 
+Therefore the total flux from GRB 990123 at peak intensity was 9.866 photons for every $cm^{2}$ each second.
+The illuminated area in the simulation was 3600 cm$^{2}$.
+Thus the simulated 10.000 photons correspond to 282 $\mu$s.
+Therefore the number of particles detected in the simulation had to be multiplied by 3551.76 to achive the countnumber for a second.
+
+\begin{figure}[htbp]
+ \centering % \begin{center}/\end{center} takes some additional vertical space
+ \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/gamma0mac.png}
+ \qquad
+ \includegraphics[width=.45\textwidth,origin=c]{images/gamma17mac.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ \caption{\label{fig:band500e}  }
+ \end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=130.0mm]{images/gammashittingsat.png}
+\label{eq:bandfunc}
+\end{center}
+\end{figure}
+
 \subsection{Simulation of the cosmic background in space}
 
-In order to understand what would give the measured background of the satellites, cosmic and solar protons and electrons were simulated in the same way as the $\gamma$ particles were in sec.
+In order to understand what would give the measured background of the satellites, cosmic and solar electrons were simulated in the same way as the $\gamma$ particles were in sec.
 \ref{sec:grb}.
@@
 
-\subsubsection{Proton background}
-
-The AE-8 model was used in SPENVIS to obtain the spatially avaraged proton energy spectra for an altitude of 500 km both for solar minimum and maximum.
+%\subsubsection{Proton background}
+
+%500km\_protons\_max.txt 
+%13535.1
+%minimum
+%12076.5
+
+%In order to include the resonances in the cross section of the hadron-hadron interactions, additional physics models are needed to be included in the simulation.
+The signal induced by these resonances might affect the measurement of the protons.
+
+%The AE-8 model was used in SPENVIS to obtain the spatially avaraged proton energy spectra for an altitude of 500 km both for solar minimum and maximum.
 The inclination of the orbit was chosen to be 89 $^{\circ}$.
@@
 
-In order to include the resonances in the cross section of the hadron-hadron interactions, additional physics models are needed to be included in the simulation.
+%In order to include the resonances in the cross section of the hadron-hadron interactions, additional physics models are needed to be included in the simulation.
 The signal induced by these resonances might affect the measurement of the protons.
 
-\begin{figure}[htbp]
- \centering % \begin{center}/\end{center} takes some additional vertical space
- \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_500km_AE-8_MIN_averaged_spectra.png}
- \qquad
- \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AE-8_MAX_averaged_spectra.png} 
+%\begin{figure}[htbp]
+% \centering % \begin{center}/\end{center} takes some additional vertical space
+% \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/alt_500km_AE-8_MIN_averaged_spectra.png}
+% \qquad
+% \includegraphics[width=.45\textwidth,origin=c]{images/alt_500km_AE-8_MAX_averaged_spectra.png} 
  % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:band500e} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of electrons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
- \end{figure}
+% \caption{\label{fig:band500e} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of electrons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
+% \end{figure}
+
+%\begin{figure}[htbp]
+% \centering % \begin{center}/\end{center} takes some additional vertical space
+% \includegraphics[width=0.45\textwidth,origin=c,angle=0]{images/protons0mac.png}
+% \qquad
+% \includegraphics[width=.45\textwidth,origin=c]{images/protonshittingsat.png} 
+ % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
+ % and rotate (angle) and image (and much more)
+ %\caption{\label{fig:band500e}}
+ %\end{figure}
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=130.0mm]{images/gammashittingsat.png}
+%\label{eq:bandfunc}
+%\end{center}
+%\end{figure}
 
 \subsection{Electron background}
+
+%500km\_electrons\_min.txt
+%1.19384e+06
+%500km\_electrons  
+%2.69537e+06
+
+Electrons
+'Trapped electron model: AE-8 MIN'
+%'Energy','MeV','Energy'
+%'IFlux','cm^-2 s^-1','Integral Flux'
+%'DFlux','cm^-2 s^-1 MeV^-1','Differential Flux'
 
@@
 
-Gabor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations.
+G\'abor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations.
 Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated.
-András Pál made vital comments on the description of the electronics.
 Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.

### 2018-05-25 msc_diploma_cubesat_galgoczi.tex
tt

@@
 
-The build up of the satellite is quite complex, consisiting of 9 modules, each with a specific material composition.
+The build up of the satellite is quite complex, consisiting of 7 modules, each with a specific material composition.
 Therefore the CAD model of the satellite was imported into Geant4 in order to understand how the satellite itself would affect the measurements.
@@
 
-We are designing a fleet of nanosatellites to perform accurate position determinations
-of short-duration gamma-ray bursts by measuring arrival time differences.
-To achieve sufficient photon statistics to measure the arrival times
-precisely under the severe limitations of size, mass, and power consumption,
-we propose the use of a large-area CsI scintillator that has high light output
-and the use of a small-sized multipixel photon counter (MPPC) that has low
-power consumption. We plan to use one of the latest-model MPPCs provided
-by Hamamatsu Photonics, which has an active area of 6  6 mm2.
+%We are designing a fleet of nanosatellites to perform accurate position determinations of short-duration gamma-ray bursts by measuring arrival time differences.
+To achieve sufficient photon statistics to measure the arrival times precisely under the severe limitations of size, mass, and power consumption, we propose the use of a large-area CsI scintillator that has high light output and the use of a small-sized multipixel photon counter (MPPC) that has low power consumption.
+We plan to use one of the latest-model MPPCs provided by Hamamatsu Photonics, which has an active area of 6  6 mm2.
 We have compared the performance of two scintillators of different sizes (150 75  5 mm3 and 100  75  5 mm3); the bigger one is the maximum size that can be mounted on a three-unit satellite, according to CubeSat standards.
@@
 \caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
+\label{fig:this_set}
 \end{figure}
@@
 
-The geometry of the two channel read out setup was simulated
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=160.0mm]{images/2channel.png}
+In order to simulate the satellite with the two channel read out setup, first this configuration was tested.
+The simulation of this setup can be seen in fig.
+\ref{fig:sim2ch}.
+The $\gamma$ source was collimated with a lead sheet that was drilled.
+The optical photons that were detected are shown only.
+The two read volumes correspond to the MPPCs.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=130.0mm]{images/2channel.png}
 \caption{Simulation of 100 $\gamma$s emitted from the source.
@@
 Only the photons that were detected are drawn.}
-\label{fig:sim_setup}
+\label{fig:sim2ch}
 \end{figure}
@@
 The tesselation was done by the TETGEN \cite{tetgen} software.
-
-\begin{figure}[h!]
-\includegraphics[width=150.0mm]{images/satellite_rad.png}
-\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
-\end{figure}
 
@@
 SP	& 	570		& Solar Panel	& 	100\\\hline
-Payload	& 	1100	& 	As you wish	& 	100\\
+Payload	& 	100	& 	Aluminum 7075-T73	& 	100\\
  \hline
@@
 \caption{The mass ratio of materials that are used for the satellite}
+\label{table:materials}
+
 \end{table}
+
+\pagebreak
+
+The material composition of the satellite can not be exported to Geant4 from CAD files directly.
+Therefore an avarage material composition was calculated for all the modules.
+In table $\ref{table:materials}$ the material composition of the 7 modules are listed.
+These materials, mostly alloys consist of several elements.
+The Geant4 cross section database is built up for elements.
+Therefore these materials had to be broken down to elements.
 
@@
 Material name & &&&&&&&&&&& \\\hline
-
 Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
@@
 \end{center}
-\caption{The chemical composition of materials that are used for the satellite}
+\caption{The chemical composition of materials in mass fraction that are used for the satellite}
 \end{table}
 
+In fig.
+\ref{fig:sat_rad} the simulation of the satellite and the two channel read out setup can be seen.
+100 $\gamma$ particles were used to shoot the satellite with a beam parralel to the plane of the scintillator.
+A scattered $\gamma$ particle can be seen being scattered into the scintillator and being detected.
+
+\begin{figure}[h!]
+\includegraphics[width=150.0mm]{images/satellite_rad.png}
+\caption{The satellite radiated by a parallel beam of 100 $\gamma$ particles. The scattered $\gamma$s induce signal in the detector.}
+\end{figure}
+\label{fig:sat_rad}
+
 \pagebreak
@@
 \subsection{Comparison of the results of the simulation with experiments}
-
-\pagebreak
 
@@
 This configuration with a lead sheet was built up in Geant4 (fig.
-\ref{fig:sim_setup} and 3.6 million $\gamma$s were simulated at each position.
+\ref{fig:this_set} and 3.6 million $\gamma$s were simulated at each position.
 
@@
 %ADC / energy calibration from measurement 20170829 illetve az egy chanellel: grb\_status3 
+\begin{center}
 
 \begin{table}[h!]
-\begin{center}
 \begin{tabular}{ |c|c|c|c|c|c|c|c|c|c| } 
@@
 \end{tabular}
- \caption{The position of the Gaussian peak fitted to the 60 keV peak of the Am source for several irradiated positions}
+ \caption{The position of the Gaussian peak fitted to the 60 keV peak of the Am source for several irradiated positions. The last set of parameters fit the experimental data.}
  \label{tabl:simulated}
+\end{table}
 \end{center}
-\end{table}
-
-\subsubsection{Calibration of photon yield}
+
+\subsubsection{Calibration of the photon yield}
 
@@
 \caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
+\label{fig:sim_res_calib}
 \end{figure}
@@
 Therefore the number of particles detected in the simulation had to be multiplied by 3551.76 to achive the countnumber for a second.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=130.0mm]{images/gammashittingsat.png}
+\label{eq:diffpos}
+\caption{The number of detections from the 10.000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
+\end{center}
+\end{figure}
+
+As one expects the most $\gamma$s ($\sim$ 200) are detected when these particles hit the scintillator directly, with a perpendicular direction to the surface of the satellite.
+The effective area of the scintillator is the largest in this case and the $\gamma$s are not absorbed by the material of the satellite.
+
+The worst case scenario is then the $\gamma$s hit the satellite with a direction parallel with the plane of the scintillator.
+Although some detections ($\sim$ 20) occur even in this case because $\gamma$s that scatter in the material of the satellite can be detected.
+In fig.
+\ref{fig:diffpos} one can see the number of detections from 10.000 $\gamma$s shot at the detector for a given position of the GRB.
+
+In fig.
+$\ref{fig:mac17hits}$ one can see the comparison between the energy spectrum measured when the $\gamma$s hit the scintillator with a perpendicular direction and when they hit the satellite from behind.
+The difference between these two scenarious is that $\gamma$s had to travel through the material of the satellite in the second case.
+About 60 \% of gammas are lost do the absorption of the satellite.
 
@@
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:band500e}  }
- \end{figure}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=130.0mm]{images/gammashittingsat.png}
-\label{eq:bandfunc}
-\end{center}
+ \caption{The measured spectrum when the $\gamma$s had to pass through the material of the satellite (right) and when they hit the scintillator directly (left)  \label{fig:mac17hits}}
  \end{figure}
@@
 
-Electrons
-'Trapped electron model: AE-8 MIN'
 %'Energy','MeV','Energy'
@@
 The inclination of the orbit was chosen to be 89 $^{\circ}$.
-At the moment hadron resonances are not taken into account in the simulation.
+%At the moment hadron resonances are not taken into account in the simulation.
 
@@
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:band500p} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of protons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
- \end{figure}
+ \caption{\label{fig:electrs} The spatially avaraged band function (differential flux for a given energy band, solid line) and the integrated band function (dotted line) of protons at an altitude of 500 km for solar minimum (left) and solar maximum (right) }
+ \end{figure}
+
+The integrated and differential spectra of electrons can be seen in fig.
+\ref{fig:electrs}.
+For the simulation the worst case scenario, the spectrum at solar maximum was utilized.
+Fig.
+\ref{fig:iii} shows the energy spectrum for the simulation of 0$^{\circ}$ when electrons hit the scintillator with a perpendicular direction.
 
@@
 % and rotate (angle) and image (and much more)
-\caption{\label{fig:i} The spectrum measured when the electrons were shot perpendicular to the scintillator (called angle of 0 $^{\circ}$)}
-\end{figure}
-
-\begin{figure}[h!]
-\centering % \begin{center}/\end{center} takes some additional vertical space
-\includegraphics[width=.3\textwidth,origin=c,angle=0]{images/satellite.png}
-\qquad
-\includegraphics[width=.5\textwidth,origin=c,angle=90]{images/8mac.png} 
-% "\includegraphics" from the "graphicx" permits to crop (trim+clip)
-% and rotate (angle) and image (and much more)
-\caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
-\end{figure}
+\caption{\label{fig:iii} The spectrum measured when the electrons were shot perpendicular to the scintillator (called angle of 0 $^{\circ}$)}
+\end{figure}
+
+The total flux from the spectrum taken from SPENVIS (fig. \ref{fig:electrs})for 1 s and a cm$^{2}$ was 2.695.370.
 
@@
 
-The results show...
-
-Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic protons and electrons at the altitude of 500km.
+Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at the altitude of 500km.
 The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123.
@@
 This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
+
+The results of the simulation of the full satellite shows that the satellite is clearly capable of detecting a GRB with a high signal to noise ratio.
+The effect of absorption can reduce the light yield by 60 \%.
+The effect of the electron background was also quantified.
+It is negligable with comparison to the signal induced by the $\gamma$ of the GRBs.
 

### 2018-05-28 msc_diploma_cubesat_galgoczi.tex
aa

@@
 
-The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs with the Constellation Gamma (Camelot)  CubeSats (miniaturized satellites).
+The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs with the Constellation Gamma (Camelot) CubeSat(s) (miniaturized satellites) being developed by C3S LLC, Budapest.
 The Geant4 simulation described in this paper also predicts the background signal originating from solar and cosmic protons and electrons.
@@
 
+The CAMELOT satellite platform is being developed by C3S LLC, Budapest.
 There would most likely be four scintillators on the CAMELOT satellite.
@@
 \includegraphics[width=130.0mm]{images/satellite_modules.png}
-\caption{The modules of the satellite}
+\caption{The modules of the satellite (Courtesy of C3S LLC) \cite{drawing}}
 \end{figure}
@@
 \includegraphics[width=130.0mm]{images/scint_on_sate.png}
-\caption{Side extensions including of the CAMELOT satellite (left) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right)}
+\caption{Side extensions including of the CAMELOT satellite (left, Courtesy of C3S LLC) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
 \label{fig:scints}
@@
 \label{fig:spectras_meas}
-\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out}
+\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out \cite{kento}}
 \label{fig:spectra}
@@
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right}
+ \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right \cite{kento}}
  \end{figure}
@@
 \includegraphics[width=80.0mm]{images/1channelelectronics.png}
-\caption{The schematic design of the readout of the MPPC for the 1 channel configuration}
+\caption{The schematic design of the readout of the MPPC for the 1 channel configuration \cite{kento}}
 \label{fig:el1ch}
@@
 \includegraphics[width=80.0mm]{images/2channelelectronics.png}
-\caption{The schematic design of the readout electronics of the 2 channel setup}
+\caption{The schematic design of the readout electronics of the 2 channel setup \cite{kento}}
 \end{figure}
@@
 \includegraphics[width=150.0mm]{images/irradiation.png}
-\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
+\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image \cite{kento}}
 \label{fig:this_set}
@@
 \includegraphics[width=130.0mm]{images/2channelsetup.png}
-\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
+\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator \cite{kento}}
 \label{fig:schem2c}
@@
  % and rotate (angle) and image (and much more)
- \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
+ \caption{\label{fig:i} The CAD model of the satellite \cite{drawing} (on the right, Courtesy of C3S LLC) and the view of the imported model in Geant (on the left)}
  \end{figure}
@@
 \end{center}
-\caption{The mass ratio of materials that are used for the satellite}
+\caption{The mass ratio of materials that are used for the satellite (Courtesy of C3S LLC) \cite{drawing}}
 \label{table:materials}
@@
 \end{center}
-\caption{The chemical composition of materials in mass fraction that are used for the satellite}
+\caption{The chemical composition of materials in mass fraction that are used for the satellite (Courtesy of C3S LLC) \cite{drawing}}
 \end{table}
@@
 \includegraphics[width=80.0mm]{images/positions.png}
-\caption{The positions of irradiation for the investigation of the response of the scintillator}
+\caption{The positions of irradiation for the investigation of the response of the scintillator  \cite{kento}}
 \end{figure}
@@
 \includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
-\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
+\caption{The spectra of 11 million photons taken experimentally \cite{kento} (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
 \label{fig:sim_res_calib}
@@
 In order to quantify the detection, the number of particles detected was used as a measure.
-10.000 $\gamma$ particles were shot at the detector paralelly on an area of 60cm x 60cm from several angles around the longitudinal axis of the satellite.
+10,000 $\gamma$ particles were shot at the detector paralelly on an area of 60cm x 60cm from several angles around the longitudinal axis of the satellite.
 This way the self absorption of the satellite was quantified.
@@
 
-Therefore the total flux from GRB 990123 at peak intensity was 9.866 photons for every $cm^{2}$ each second.
+Therefore the total flux from GRB 990123 at peak intensity was 9,866 photons for every $cm^{2}$ each second.
 The illuminated area in the simulation was 3600 cm$^{2}$.
-Thus the simulated 10.000 photons correspond to 282 $\mu$s.
+Thus the simulated 10,000 photons correspond to 282 $\mu$s.
 Therefore the number of particles detected in the simulation had to be multiplied by 3551.76 to achive the countnumber for a second.
@@
 \includegraphics[width=130.0mm]{images/gammashittingsat.png}
-\label{eq:diffpos}
-\caption{The number of detections from the 10.000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
+\caption{The number of detections from the 10,000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
+\label{fig:diffpos}
 \end{center}
@@
 The effective area of the scintillator is the largest in this case and the $\gamma$s are not absorbed by the material of the satellite.
+The detection rate would be 6,393,168 $\frac{Hz}{cm^{2}}$ at peak flux.
 
@@
 In fig.
-\ref{fig:diffpos} one can see the number of detections from 10.000 $\gamma$s shot at the detector for a given position of the GRB.
+$\ref{fig:diffpos}$ one can see the number of detections from 10,000 $\gamma$s shot at the detector for a given position of the GRB.
 
@@
 
-The total flux from the spectrum taken from SPENVIS (fig. \ref{fig:electrs})for 1 s and a cm$^{2}$ was 2.695.370.
-
-\begin{figure}[h!]
-\includegraphics[width=150.0mm]{images/electronabsorption.png}[H!]
-\caption{The ammount of electrons detected from 100.000 shoot in the simulation}
+\pagebreak
+
+The total flux from the spectrum taken from SPENVIS (fig.
+\ref{fig:electrs}) for 1 s and a cm$^{2}$ was 1,226,000.
+Therefore in order to obtain the count rate, the values obtained for the simulation of 1,000,000 electron with different directions have to be avaraged and multiplied by 1.226 $\cdot$ 3600, which yields 230,478 counts each second.
+
+\begin{figure}[h!]
+\includegraphics[width=150.0mm]{images/electronabsorption.png}
+\caption{The ammount of electrons detected from 1,000,000 shoot in the simulation}
 \end{figure}
@@
 The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123.
-The induced signal of these particles was determined.
+The induced signal of these particles was determined, which is about one order of magnitude lower then the signal of a GRB.
 This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
@@
 Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated.
+The model of the satellite was provided by Tarcai Norbert and Wágner Olivér from C3S LLC.
 Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.
@@
 
+\bibitem{drawing} Private communication, C3S LLC.
+
+\bibitem{kento} Master thesis, K. Torigoe, N. Werner, Y. Fukazawa, N. Uchida, K. Tanaka, T. Mizuno \& H. Takahashi, School of Science, Hiroshima University,
+
+%\bibitem{kento} Master thesis, K. Torigoe, Norbert Werner, Yasushi Fukazawa, Nagomi Uchida, Koji Tanaka, Tsunefumi Mizuno \& Hiromitsu Takahashi, School of Science, Hiroshima University,
+
 \bibitem{grb42} Hurley K., Mitrofanov I. G., Golovin D., et al. 2013, EAS Publications Series, 61, 459

### 2018-05-28 msc_diploma_cubesat_galgoczi.tex
aa

@@
 Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated.
-The model of the satellite was provided by Tarcai Norbert and Wágner Olivér from C3S LLC.
+The model of the satellite was provided by Norbert Tarcai and Olivér Wágner from C3S LLC.
+The experimental data that was needed for the simulation was provided by Kento Torigoe and his colleges from the University of Hiroshima.
+The energy spectrum of cosmic electrons was deduced by Jakub Ripa.
 Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.

### 2018-05-28 msc_diploma_cubesat_galgoczi.tex
aa
text

@@
 %standard
-\geometry{left=3.0cm,right=3.0cm,top=2.0cm,bottom=2.0cm}
+\geometry{left=3.2cm,right=3.2cm,top=2.3cm,bottom=2.3cm}
 
@@
 
-\vspace{2.5 cm}
+\vspace{1.5 cm}
 \large \textbf {2018}\\
@@
 
-The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs with the Constellation Gamma (Camelot) CubeSat(s) (miniaturized satellites) being developed by C3S LLC, Budapest.
-The Geant4 simulation described in this paper also predicts the background signal originating from solar and cosmic protons and electrons.
-
-First the parameters of the simulation had to be fine tuned to reproduce the measured spectra in the laboratory.
-The simulation of the number of optical photons being deteted was sufficent to predict the signal as the electronic amplification is linear.
-
-The build up of the satellite is quite complex, consisiting of 7 modules, each with a specific material composition.
-Therefore the CAD model of the satellite was imported into Geant4 in order to understand how the satellite itself would affect the measurements.
-The "calibrated" scintillator afterwards was placed on the side of the satellite.
-
-Three cases were investigated.
-First, the model of the detector and the satellite was radiated with a parallel gamma beam that had the same parameters as GRB 9900123, the reference GRB chosen.
-The position of the source was rotated spherically around the satellite.
-In this way the absorbtion of $\gamma$s in the material of the satellite was investigated.
-
-Secondly the cosmic background induced by the protons and electrons was simulated.
-The energy spectrum of electrons and protons was obatined from the SPENVIS information system.
-The satellite was radiated with these given energy distributions and fluxes.
+The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs for the CAMELOT (Cubesats Applied for MEasuring and LOcalising Transients) mission.
+This CubeSat (miniaturized satellite) is being developed by C3S LLC, in Budapest.
+The Geant4 simulation described in this paper also predicts the background signal originating from solar and cosmic electrons.
+
+The simulation was first validated by comparing the spectrum of an $^{241}$Am source measured in laboratory with the spectrum obtained with the simulation.
+Secondly the photon yield dependence of the position of the source above the scintillator detector was determined by the simulation.
+The results agreed with the experimental data.
+
+The satellite consists of seven modules, each with a specific material composition.
+Therefore the CAD model of the satellite had to be imported into the simulation in order to understand how the satellite itself would affect the measurements.
+The validated scintillator afterwards was placed on the side of the satellite in the simulation.
+
+The detector and the satellite was radiated with a parallel $\gamma$-rays.
+The energy spectrum of these particles was chosen to be the same as GRB 9900123.
+In order to understand  how the satellite would absorb the $\gamma$-rays several simulations were carried out by chaning the incident angle of the beam around the longitudinal axis of the satellite.
+
+Secondly the effect of solar and cosmic electrons was investigated.
+The satellite was radiated by electrons with an energy distribution obtained from the SPENVIS information system.
+This distribution represents the energy spectrum of electrons in polar orbit 500 km above the surface of Earth.
 
@@
 
-Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} are one of the most invesitaged and yet less understood astrophysical objects.
-The have been studied for more than fourty years as one of the most extreme explosive events in the Universe.
+Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} are one of the most invesitaged and yet least understood astrophysical objects.
+They have been studied for more than fourty years as one of the most extreme explosive events in the Universe.
 Their origin is still not yet fully understood.
-GRBs were discovered in years 1967–73 by military satellites.
+GRBs were discovered in 1967–73 by military satellites.
 The scientific community only got to know their existance in the early seventies \cite{grb5}.
-A GRB event is brighter than any other object in the sky during their appearance that can last from millisecond to minutes.
-Every day the a new GRB is observed by the satellites investigating them.
-The main part of the energy spectrum of these events is from the keV to the MeV ranges.
+A GRB event is brighter than any other object in the sky during its appearance that can last from a millisecond to minutes.
+Every day a new GRB is observed by the satellites investigating them.
+The main part of the energy spectrum of these events in the keV to the MeV ranges.
 
@@
 The second group of GRBs are called short GRBs as their prompt $\gamma$-ray emission lasts $\leqslant$2 s.
-These objects also pocess a harder spectrum.
+These objects also posess a harder spectrum.
 They were linked to the merge of two very compact objects, such as neutron star - neutron star (NS-NS) and neutron star - black hole (NS-BH) mergers \cite{grb9}.
@@
 
-One of the most accepted theories describe GRBs as collisions of highly relativistic outflow of the accelerated jetted matter \cite{grb10}.
-For most of the observed GRBs the prompt $\gamma$-ray emission was followed by longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11}.
+One of the most accepted theories describe GRBs as collisions of highly relativistic outflow of the accelerated jets \cite{grb10}.
+For most of the observed GRBs the prompt $\gamma$-ray emission was followed by a longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11}.
 This is due to the propagation of a relativistic shockwave through the medium that surrounds the burst.
-Obsrvations proved that GRBs are at cosmological distances \cite{grb12}.
+Observations proved that GRBs are at cosmological distances \cite{grb12}.
 The farthest GRB observed was at a distance of z=9.4.
@@
 The long GRBs are even farther away, on avarage at z=2.
-The energy that is released is tremendous, about 10 erg.
-Long GRBs have been linked to the brightest regions of galaxies that contains the the most massive stars \cite{grb14}.
+The energy that is released in such an event is tremendous, about 10 erg.
+Long GRBs have been linked to the brightest regions of galaxies those contain the the most massive stars \cite{grb14}.
 %The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5].
@@
 On the contrary, short GRBs are thought to originate in old populations.
-The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves of such an event.
+The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves of such events.
 This was detected by the LIGO/Virgo collaboration in 2017 \cite{gravwave}.
@@
 \item{Classification: some of the observed light curves can not be classified into short and long GRBs, such as the ultra-long GRBs.}
-\item{Central engine: in most cases it is thought that a black hole is formed after the merging of neutron stars and core collapse of massive starts.
+\item{Central engine: in most cases it is thought that a black hole is formed after the merging of neutron stars and core collapse of massive stars.
 Although there are models that predict the birth of a magnetar.
 The most exotic theories predict the birth of a quark star that has never yet been observed.}
-\item{Acceleration mechanism of the jets: How particles are accelerated to a velocity of Lorentz-factor of 300 in the shock waves is not yet understood.}
+\item{Acceleration mechanism of the jets: How particles are accelerated to a velocity of a Lorentz-factor of 300 in the shock waves is not yet understood.}
 \item{GRB jet composition: there are two possible driving forces behind the acceleration of jet material.
 The first one is magnetic field dominated and the other one is dominated by baryons.
-As the acceleration of particles is not yet fully understood, it is not known whether protons can be accelerated to ultra-high energies.
+As the acceleration of particles is not yet fully understood, it is not known whether protons can be accelerated to ultra-high energies or not.
 These could produce Ultra-High Energy Cosmic Rays.}
@@
 \item{First stars: different population of stars on avarage have different masses.
-Models predit that population III stars end their life with a black hole that has a mass about ten times bigger than population I and II stars.
-The progenitors of GRBs can be classified into populations by their redshift \cite{grb20}.}
+Models predict that population III stars end their life with a black hole that has a mass about ten times bigger than population I and II stars.
+The progenitors of GRBs can be classified into populations by their redshifts \cite{grb20}.}
 
@@
 This historical detection occured on August 17, 2017.
-The Fermi satellite detected the (short) GRB 170817A, approximately 1.7 s before to the detection of the GRB, LIGO-Virgo detector network observed a GW signal GW170817.
+The Fermi satellite detected the (short) GRB 170817A, approximately 1.7 s after the LIGO-Virgo detector network observed a GW signal GW170817.
 The origin of this source was a neutron-neutron star merger.
@@
 As LIGO is constantly upgrading its detectors, gravitational waves will be detected more often.
-An even more sensitive gravitational wave detector is under building callled Kamioka Gravitational Wave Detector (KAGRA).
-First scientific measurements will be taken in the 2020s \cite{grb26}.
+An even more sensitive gravitational wave detector is under construction, callled Kamioka Gravitational Wave Detector (KAGRA).
+First scientific measurements will be taken in the 2020s \cite{grb26} with this device.
 
@@
 Several types of detectors can be used for detecting $\gamma$ photons\cite{grb30}, for example the semiconductor based  German Position Sensitive Proportional Counters (PSPC) of the ROSAT X-ray telescope.
-For our satellite the size of the detector is limited, therefore the best option was the usage of scintillators.
+For our satellite the size of the detector is limited, therefore the best option was to choose scintillators.
 Mostly used scintillators in space include inorganic crystal scintillators, for example NaI(Tl) or CsI(Tl), and plastic scintillators.
-CsI(Tl) was chosen as the detector of the Camelot CubeSat due to it's high light yield.
+CsI(Tl) was chosen as the detector of the Camelot CubeSat due to its high light yield.
 
@@
 This subsection provides an overview of the existing missions that are aimed to detect GRBs.
-Field of view (FOV) an localization accuracy are chosen to compare them with the Camelot CubeSat.
+Field of view (FOV) and localization accuracy are chosen to compare them with the Camelot CubeSat.
 The proposed design of the Camelot satellite has the advantage of a large field of view and a high localization accuray.
@@
 By measuring the time difference between the triggering of each satellite, the GRB soure can be triangularized.
-By using more satellites, the field of view will be the full-sky and localization accuracy increases.
+By using more satellites, the field of view becomes full-sky and localization accuracy increases.
 
 The planed localization accuracy is more precise than any other existing GRB mission, that might reach $\sim$10'.
-While providing the highest lcoalization accuray, the field of view would also the be the highest, even larger than the field of view of the INTEGRAL/SPI-ACS and Fermi.
+While providing the highest lcoalization accuracy, the field of view would also be the highest, even larger than the field of view of the INTEGRAL/SPI-ACS and Fermi.
 
@@
 \includegraphics[width=130.0mm]{images/fovvsloc.png}
-\caption{The field of view and localization accuracy of several missions including the Camelot CubeSat.}
+\caption{The field of view and localization accuracy of several missions including the CAMELOT CubeSat.}
 \end{figure}
@@
 \begin{itemize}
-\item Fermi 7 \cite{grb28} was launched in 2008 and its main instruments are Gamma-ray Burst Monitor and the Large Area Telescope (LAT). 
-\item Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 and its main instruments are Burst Alert Telescope (BAT), X-ray Telescope (XRT), and UV/Optical Telescope (UVOT).
+\item Fermi 7 \cite{grb28} was launched in 2008 and its main instruments are the Gamma-ray Burst Monitor and the Large Area Telescope (LAT). 
+\item Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 with its main instruments, those are the Burst Alert Telescope (BAT),  the X-ray Telescope (XRT), and the UV/Optical Telescope (UVOT).
 \item INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 \cite{grb32} was launched in 2002.
@@
 \item CALorimetric Electron Telescope (CALET) 12 \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
-\item Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. The instrument is placed on ISS.
-\item Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of GRB polarization.
+\item Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. This instrument is placed on ISS.
+\item Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of $\gamma$-rayGRB polarization.
 \item Lomonosov 15 /BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
-\item The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39}, was launched in 2017.
-It has on board the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
-\item ASTROSAT 17 \cite{grb40}, was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
+\item The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39} was launched in 2017.
+It has the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
+\item ASTROSAT 17 \cite{grb40} was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
 \item Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 \cite{grb41}, was launched in 2002.
@@
 
-The CAMELOT satellite platform is being developed by C3S LLC, Budapest.
+The CAMELOT satellite platform is being developed by C3S LLC, in Budapest.
 There would most likely be four scintillators on the CAMELOT satellite.
 On two neighbouring sides of the satellite have two scintillators each.
-The scintillator will have a case either from aluminium or carbon fibre.
+The scintillators will have a case either from aluminium or carbon fibre.
 
@@
 
-The Camelot satellite will consist of the following modules:
+The CAMELOT satellite will consist of the following modules:
 
 \begin{itemize}
-\item On-Board Computer [OBC] is responsible for control all the satellite’s sub-systems. OBC collects housekeeping and payload data and archives them in its internal storage.
+\item On-Board Computer [OBC] is responsible for the control of all the satellite’s sub-systems. OBC performs housekeeping and collects payload data and archives it in its internal storage.
 \item Electrical Power System [EPS] is responsible for managing primary and secondary power sources and distributing power at appropriate voltage levels to on-board subsystems.
 \item COM UHF Transceiver [COM] provides an RF communication link between the Ground Segment and the satellite.
-The COM codes the received messages from the OBC and transmits to the Ground Segment.
-Furthermore, the COM decodes the received RF messages from the Ground Segment and transmits to the OBC.
-\item Attitude Determination and Control System [ADCS] determines and controls the satellite attitude.
-\item Auxiliary Electronics [AUX] subsystems control the deploying mechanisms and monitor the
-solar arrays. The Aux subsystem also contains the rigid backplane of the satellite; therefore, it also connects the subsystems.
+The COM codes are received messages from the OBC and are transmitted to the Ground Segment.
+Furthermore, the COM decodes the received RF messages from the Ground Segment and transmits them to the OBC.
+\item Attitude Determination and Control System [ADCS] determines and controls the altitude of the satellite.
+\item Auxiliary Electronics [AUX] subsystems control the deploying mechanisms and monitor the solar arrays.
+The Aux subsystem also contains the rigid backplane of the satellite; therefore, it also connects the subsystems.
 \item Structure [STRU]
@@
 \includegraphics[width=130.0mm]{images/scint_on_sate.png}
-\caption{Side extensions including of the CAMELOT satellite (left, Courtesy of C3S LLC) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
+\caption{Side extensions including the CAMELOT satellite (left, Courtesy of C3S LLC) where scintillators are placed and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
 \label{fig:scints}
@@
 Two factors play role here, the self absorption of the reflectivity of the tape that is used to cover the scintillator.
-The length of the self absoprtion is in the order of a meter and the reflectivity of the ESR tape, which is above 99 \% can be seen in fig.
+The length of the self absorption is in the order of a meter and the reflectivity of the ESR tape, which is above 99 \% can be seen in fig.
 \ref{fig:refl}.
-The idea that we came is using two MPPC-s with coincidence.
+The idea that we came up is using two MPPC-s with coincidence.
 This results in a smaller leakage current (noise) as the noise has a poissonian statistic.
@@
 The most used software in particle physics are MCNPX, FLUKA and Geant4.
-For this thesis Geant4 was chosen as it is the best for simulation of several types of particles at the same time and building up the geometry of detectors is most propably is the most convinient in the software.
+For this thesis Geant4 was chosen as it is the best for simulation of several types of particles at the same time and building up the geometry of detectors is most propably is the most convinient in this software.
 
@@
 Its development, maintenance and user support are taken care by the international Geant4 Collaboration.
-Areas in science that has used Geant4 are vary wide from the design of complex medical machines to accelerator, nuclear physics, hight energy physics and space applications.
+Areas in science that has used Geant4 are vary widely from the design of complex medical machines to accelerator, nuclear physics, high energy physics and space applications.
 Several thousand people use it all around the globe.
@@
 
-In order to understand and charaterize the behaviour of the large-area CsI(Tl) scintillator detector and the MPPC readout an experimental setup was built in Hiroshima, Japan.
+In order to understand and charaterize the behaviour of the large-area CsI(Tl) scintillator detector and the MPPC readout; an experimental setup was built in Hiroshima, Japan.
 The experimental setup provided vital information for the simulation, mostly for the position dependence of the light yield.
@@
 In fig.
-\ref{fig:refl} the reflectivity of this tape can be seen depending on the wavelenght of the photons, exceeding 99 \% for most of the wavelengths.
+\ref{fig:refl} the reflectivity of this tape can be seen depending on the wavelength of the photons, exceeding 99 \% for most of the relevant spectrum.
 It is important as the optical photons have to be reflected several times in order to be read out with the small effective are of the MPPC.
@@
 The CsI(Tl) scintillator used is produced by AmCrys \cite{scinti}.
-The dimension of this detector are 150 mm x 75 mm x 5 mm, the largest possible size that can fit onto the surface of the detector.
+The dimension of this detector are 150 mm x 75 mm x 5 mm, the largest possible size that can fit onto the surface of the satellite.
 The spectra of the optical photons produced in the scintillation process can be seen in fig.
@@
 For the single MPPC readout setup a commercial charge-sensitive preamplifier (CLEAR-PULSE 5028), a shaping amplifier (EG\&G ORTEC 571), and an ADC (AMPTEC MCA800A) were used to obtain an electric signal read out by a PC.
-The shaping times was set to 1 $\mu$s.
+The shaping time was set to 1 $\mu$s.
 
@@
 In fig.
-\ref{fig:schem2c} this setup can be seen with the MPPCs placed symmetrically to the scintillator.
+\ref{fig:schem2c} this setup can be seen with the MPPCs placed symmetrically onto the scintillator.
 
@@
 
+\pagebreak
+
 In fig.
@@
 \section{Results of the simulation}
-
-\subsection{Comparison of the results of the simulation with experiments}
 
@@
 The AE-8 model was used in SPENVIS to obtain the spatially avaraged elextron energy spectra for an altitude of 500 km both for solar minimum and maximum.
-The inclination of the orbit was chosen to be 89 $^{\circ}$.
+The inclination of the orbit was chosen to be 89$^{\circ}$.
 %At the moment hadron resonances are not taken into account in the simulation.
@@
 
-In order to simulate how the Camelot CubeSat would interact with the cosmic background and how sensitive it would be to GRBs that it is designed to investigate a Geant4 simulation was built.
+A Geant4 Monte-Carlo based simulation was developed in order to understand how the CAMELOT CubeSat would detect $\gamma$-rays originating from short GRBs.
+The effect of solar and cosmic electrons on the satellite was also investigated with the simulation.
 
 As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the particle detector of the satellite -- was implemented in Geant4.
-The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs that was used to read out the scintillator.
+The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs in the simulation with experimental data.
 After the calibration, the results of the simulation was capable of predicting the signal that would be measured in space.
 
-Secondly, the complex CAD model of the satellite --consisting of 7 modules, each with a give avarage material composition-- was exported to Geant4.
+Secondly, the complex CAD model of the satellite --consisting of 7 modules, each with a given avarage material composition-- was exported to Geant4.
 The scintillator and its read out was placed on the side of the satellite.
@@
 Thirdly, the $\gamma$ absorption of the satellite was invastigated.
-Parallel $\gamma$-rays with a flux and energy distribution of GRB 9900123 (fig.
+Parallel $\gamma$-rays with the energy distribution of GRB 9900123 (fig.
 \ref{fig:grb_band}) was simulated.
@@
 
-Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at the altitude of 500km.
+Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at an altitude of 500km.
 The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123.
-The induced signal of these particles was determined, which is about one order of magnitude lower then the signal of a GRB.
-This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
-
-The results of the simulation of the full satellite shows that the satellite is clearly capable of detecting a GRB with a high signal to noise ratio.
-The effect of absorption can reduce the light yield by 60 \%.
+The induced signal of these particles was determined, which is about one order of magnitude lower than the signal of a GRB.
+This signal of electrons needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
+
+The results of the simulation shows that the satellite is clearly capable of detecting a GRB with a high signal to noise ratio.
+The effect of absorption can reduce the measured light yield by 60 \%.
 The effect of the electron background was also quantified.
-It is negligable with comparison to the signal induced by the $\gamma$ of the GRBs.
+It is an order of magnitude lower to the signal induced by the $\gamma$-rays of a GRB.
 

### 2018-05-29 msc_diploma_cubesat_galgoczi.tex
text

@@
 
-\subsection{Particle detectors in space}
+\subsection{Gamma- and X-ray detectors in space}
 
@@
 \ref{fig:sim2ch}.
-The $\gamma$ source was collimated with a lead sheet that was drilled.
-The optical photons that were detected are shown only.
-The two read volumes correspond to the MPPCs.
+The $\gamma$ source was collimated with a lead sheet that was drilled in 9 places.
+The optical photons that were detected are shown only in the simulation.
+The two read out volumes (red) correspond to the MPPCs.
 
@@
 The direction of GRBs is isotropic in the sky as they are extragalactic objects.
-As the positioning of the scintillators is not decided yet it is important to understand which configuration would be the best for detecting as many GRBs as possible.
-Therefore it is vital to understand how the material of the satellite itself absorbs $\gamma$s.
+As the position of the scintillators is not decided yet it is important to understand which configuration would be the best in order to detect as many GRBs as possible.
+Therefore it is vital to understand how the material of the satellite itself absorbs $\gamma$-rays.
 The satellite consists of several modules with specific shapes and material contents.
@@
 These materials, mostly alloys consist of several elements.
-The Geant4 cross section database is built up for elements.
+The Geant4 cross section database is built up only for elements.
 Therefore these materials had to be broken down to elements.
@@
 \ref{fig:sat_rad} the simulation of the satellite and the two channel read out setup can be seen.
-100 $\gamma$ particles were used to shoot the satellite with a beam parralel to the plane of the scintillator.
-A scattered $\gamma$ particle can be seen being scattered into the scintillator and being detected.
+100 $\gamma$ particles were used to shoot the satellite with a beam parallel to the plane of the scintillator.
+A scattered $\gamma$ particle can be seen scattered into the scintillator and being detected.
 
@@
 The physical process that is behind this is the X-ray fluoresence.
-By default this process is not included in the Geant4 simulations, thus I had to turn it on.
+By default this process is not included in Geant4 simulations, thus I had to turn it on.
 A histogram with and without x-ray fluorescence can be seen in fig.
@@
 \label{tab:exp_sim}
-\caption{The position dependence of the photon yield measured at the Univeristy of Hiroshima by Kento Torigoe}
+\caption{The position dependence of the photon yield, measured at the Univeristy of Hiroshima by Kento Torigoe}
 \end{center}
@@
 The amplitude of the peaks in the energy spectrum of signal obtained by the MPPC depends mostly on three parameters.
-The absorption length of the scintillation light in the scintillator, the reflectivity of the surface and the scintillation photon yield of the scintillator.
+The absorption length of the scintillation light in the scintillator, the reflectivity of the surface and the scintillation photon light yield of the scintillator.
 In order to obtain the histogram that we would measure by the MPPC, the histogram obtained by the simulation had to be scaled up both in amplitude and energy.
@@
 Thus the simulated 10,000 photons correspond to 282 $\mu$s.
-Therefore the number of particles detected in the simulation had to be multiplied by 3551.76 to achive the countnumber for a second.
+Therefore the number of particles detected in the simulation had to be multiplied by 3551.76 to achive the count number for a second.
 
@@
 The effective area of the scintillator is the largest in this case and the $\gamma$s are not absorbed by the material of the satellite.
-The detection rate would be 6,393,168 $\frac{Hz}{cm^{2}}$ at peak flux.
-
-The worst case scenario is then the $\gamma$s hit the satellite with a direction parallel with the plane of the scintillator.
+(Only the aluminium case absorbs $\gamma$-rays in this case.) The detection rate would be 6,393,168 $\frac{Hz}{cm^{2}}$ at peak flux.
+
+The worst case scenario is when the $\gamma$s hit the satellite with a direction parallel to the plane of the scintillator.
 Although some detections ($\sim$ 20) occur even in this case because $\gamma$s that scatter in the material of the satellite can be detected.
@@
 
-The AE-8 model was used in SPENVIS to obtain the spatially avaraged elextron energy spectra for an altitude of 500 km both for solar minimum and maximum.
+The AE-8 model was used in SPENVIS to obtain the spatially avaraged electron energy spectra for an altitude of 500 km both for solar minimum and maximum.
 The inclination of the orbit was chosen to be 89$^{\circ}$.
@@
 Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at an altitude of 500km.
-The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123.
+The satellite was radiated by these particles in Geant4 in the same way that were used for the $\gamma$-rays of GRB 9900123.
 The induced signal of these particles was determined, which is about one order of magnitude lower than the signal of a GRB.
-This signal of electrons needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
+The induced signal of electrons needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
 

### 2018-05-30 msc_diploma_cubesat_galgoczi.tex
txt

@@
 
-The detector and the satellite was radiated with a parallel $\gamma$-rays.
+The detector and the satellite was radiated with a parallel beam of $\gamma$-rays.
 The energy spectrum of these particles was chosen to be the same as GRB 9900123.
-In order to understand  how the satellite would absorb the $\gamma$-rays several simulations were carried out by chaning the incident angle of the beam around the longitudinal axis of the satellite.
+In order to understand  how the satellite would absorb the $\gamma$-rays several simulations were carried out by changing the incident angle of the beam around the longitudinal axis of the satellite.
 
@@
 They have been studied for more than fourty years as one of the most extreme explosive events in the Universe.
-Their origin is still not yet fully understood.
-GRBs were discovered in 1967–73 by military satellites.
-The scientific community only got to know their existance in the early seventies \cite{grb5}.
+Their origin is still not fully understood.
+GRBs were discovered in 1967–73 by the VELA military satellites.
+The scientific community only got to know about their existance in the early seventies \cite{grb5}.
 A GRB event is brighter than any other object in the sky during its appearance that can last from a millisecond to minutes.
 Every day a new GRB is observed by the satellites investigating them.
-The main part of the energy spectrum of these events in the keV to the MeV ranges.
+The main part of the energy spectrum of these events is in the keV to the few MeV range.
 
@@
 The energy that is released in such an event is tremendous, about 10 erg.
-Long GRBs have been linked to the brightest regions of galaxies those contain the the most massive stars \cite{grb14}.
+Long GRBs have been linked to the brightest regions of galaxies those that contain the most massive stars \cite{grb14}.
 %The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5].
@@
 The diversity of the curves is extraordinary.
-Events with a length from millisecond to a second exist either with smooth or highly variable curves.}
+Events with a length from millisecond to tens of seconds exist either with smooth or highly variable light curves.}
 \end{figure}
@@
 On the contrary, short GRBs are thought to originate in old populations.
-The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves of such events.
-This was detected by the LIGO/Virgo collaboration in 2017 \cite{gravwave}.
+The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves from such an event.
+GW170818 was detected by the LIGO/Virgo collaboration in 2017 \cite{gravwave}.
 The electromagnetic counterpart of this gravitational wave event was detected as a short GRB by the Fermi/Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}.
-Short GRBs emit electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.
+Kilonovae producing infrared electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.
 
@@
 
-Despite the fact that GRBs have been studied for more than fourty years a lot of questions are still not understood about their physics\cite{grb19}.
-In the following the main open questions are listed:
+Despite the fact that GRBs have been studied for more than fourty years many questions are still not understood about their physics\cite{grb19}. In the following the main open questions are listed:
 
@@
 This subsection provides an overview of the existing missions that are aimed to detect GRBs.
-Field of view (FOV) and localization accuracy are chosen to compare them with the Camelot CubeSat.
-The proposed design of the Camelot satellite has the advantage of a large field of view and a high localization accuray.
+Field of view (FOV) and localization accuracy are chosen to compare them with the CAMELOT mission.
+The proposed design of the CAMELOT satellites has the advantage of a large field of view and a high localization accuray.
 The main idea is that each CubeSat will detect GRBs at the same time.
-By measuring the time difference between the triggering of each satellite, the GRB soure can be triangularized.
-By using more satellites, the field of view becomes full-sky and localization accuracy increases.
-
-The planed localization accuracy is more precise than any other existing GRB mission, that might reach $\sim$10'.
-While providing the highest lcoalization accuracy, the field of view would also be the highest, even larger than the field of view of the INTEGRAL/SPI-ACS and Fermi.
+By measuring the time difference between the triggering of each satellite, the GRB soure can be localized by triangulation.
+By using more than nine satellites, the constellation achieves all sky coverage and localization accuracy.
+
+The planed localization accuracy might reach $\sim$10'. While providing a good localization accuracy, the field of view would be even larger than  that of the INTEGRAL/SPI-ACS and Fermi.
 
@@
 Therefore from a fraction of the cost several satellites could be built and deployed in orbit.
-Having several satellites also provide a high redundance.
+Having several satellites also provides redundance.
 
@@
 \begin{itemize}
-\item Fermi 7 \cite{grb28} was launched in 2008 and its main instruments are the Gamma-ray Burst Monitor and the Large Area Telescope (LAT). 
-\item Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 with its main instruments, those are the Burst Alert Telescope (BAT),  the X-ray Telescope (XRT), and the UV/Optical Telescope (UVOT).
-\item INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 \cite{grb32} was launched in 2002.
+\item Fermi \cite{grb28} was launched in 2008 and its main instruments are the Gamma-ray Burst Monitor and the Large Area Telescope (LAT). 
+\item Neil Gehrels Swift Observatory (Swift) \cite{grb31} was launched in 2005 with its main instruments, those are the Burst Alert Telescope (BAT),  the X-ray Telescope (XRT), and the UV/Optical Telescope (UVOT).
+\item INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) \cite{grb32} was launched in 2002.
 The most succesfull instruments on board include are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the "Imager on Board the Integral Satellite (IBIS)" detector.
-\item Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 \cite{grb34} was launched in 2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
-\item CALorimetric Electron Telescope (CALET) 12 \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
-\item Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. This instrument is placed on ISS.
+\item Astro-Rivelatore Gamma a Immagini Leggero (AGILE)  \cite{grb34} was launched in 2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
+\item CALorimetric Electron Telescope (CALET)  \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
+\item Monitor of All-sky X-ray Image (MAXI) \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. This instrument is placed on ISS.
 \item Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of $\gamma$-rayGRB polarization.
-\item Lomonosov 15 /BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
-\item The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39} was launched in 2017.
+\item Lomonosov/BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
+\item The Hard X-ray Modulation Telescope (Insight-HXMT) \cite{grb39} was launched in 2017.
 It has the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
-\item ASTROSAT 17 \cite{grb40} was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
-\item Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 \cite{grb41}, was launched in 2002.
+\item ASTROSAT \cite{grb40} was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
+\item Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) \cite{grb41}, was launched in 2002.
 It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
@@
 The CAMELOT satellite platform is being developed by C3S LLC, in Budapest.
-There would most likely be four scintillators on the CAMELOT satellite.
-On two neighbouring sides of the satellite have two scintillators each.
+There would most likely be four scintillators on the CAMELOT satellite, on two neighbouring sides of the satellite, two scintillators each.
 The scintillators will have a case either from aluminium or carbon fibre.
@@
 These photons will be detected by Silicon Photomultiplier device called Multi Pixel Photon Counter, MPPC for short.
-This if by far the best and most compact solution as the size of cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$.
+This is by far the best and most compact solution as the size of cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$.
 The first tests were carried out by a single MPPC readout, which was followed by a design with two MPPCs to maximize the light yield and minimalize the noise.
@@
 \includegraphics[width=130.0mm]{images/scint_on_sate.png}
-\caption{Side extensions including the CAMELOT satellite (left, Courtesy of C3S LLC) where scintillators are placed and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
+\caption{Side extensions including the CAMELOT satellite (left, based on QB50 system requirements and recommendations) where scintillators are placed and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
 \label{fig:scints}
@@
 The large area and small thickness of the scintillator makes it challenging for the read out as optical photons have to be reflected several times to reach the MPPC.
-Two factors play role here, the self absorption of the reflectivity of the tape that is used to cover the scintillator.
+Two factors play a role here, the self absorption of the reflectivity of the tape that is used to cover the scintillator.
 The length of the self absorption is in the order of a meter and the reflectivity of the ESR tape, which is above 99 \% can be seen in fig.
@@
 This results in a smaller leakage current (noise) as the noise has a poissonian statistic.
-Therefore the noise is "random" and the chance of a trigger from both of the MPPC has a very low chance.
-The other advantage is the incread photon yield due to the double of the photon collection area.
+Therefore the noise is "random" and a trigger from both of the MPPC is unlikely.
+The other advantage is the increased photon yield due to the double of the photon collection area.
 The difference between one and two channel readout can be seen in fig.
-\ref{fig:spectra}.
+\ref{fig:spectras_meas}.
 
@@
 \includegraphics[width=130.0mm]{images/histo_for_det.png}
+\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out \cite{kento}}
 \label{fig:spectras_meas}
-\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out \cite{kento}}
-\label{fig:spectra}
 \end{figure}
@@
 The most used software in particle physics are MCNPX, FLUKA and Geant4.
-For this thesis Geant4 was chosen as it is the best for simulation of several types of particles at the same time and building up the geometry of detectors is most propably is the most convinient in this software.
+For this thesis Geant4 was chosen as it is the best for simulation of several types of particles at the same time and building up the geometry of detectors is propably the most convinient in this software.
 
@@
 It is an object orianted programming platform in C++.
-Its development, maintenance and user support are taken care by the international Geant4 Collaboration.
-Areas in science that has used Geant4 are vary widely from the design of complex medical machines to accelerator, nuclear physics, high energy physics and space applications.
-Several thousand people use it all around the globe.
+Its development, maintenance and user support are taken care of by the international Geant4 Collaboration.
+Areas in science that have used Geant4 vary widely from the design of complex medical machines to accelerator, nuclear physics, high energy physics and space applications.
+Several thousands of people use it all around the world.
 
@@
 
+\pagebreak
+
 \subsection{The experimental setup}
@@
 The experimental setup provided vital information for the simulation, mostly for the position dependence of the light yield.
-Different $\gamma$ source were used, mostly an $^{241}$Am source.
+Different $\gamma$ sources were used, mostly an $^{241}$Am source.
 
@@
  \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right \cite{kento}}
+ \label{fig:schem}
  \end{figure}
@@
 The CsI(Tl) scintillator used is produced by AmCrys \cite{scinti}.
-The dimension of this detector are 150 mm x 75 mm x 5 mm, the largest possible size that can fit onto the surface of the satellite.
+The dimensions of this detector are 150 mm x 75 mm x 5 mm, the largest possible size that can fit onto the surface of the satellite.
 The spectra of the optical photons produced in the scintillation process can be seen in fig.
@@
 
+\pagebreak
+
 \subsection{The readout of the detector}
@@
 The response of the MPPC detector used depends on temperature.
-Therefore the experimental setup was placed in a thermostatically controlled chamber (ESPEC LU-113) keeping the temperature at 25$^{\circ}$.
+Therefore the experimental setup was placed in a thermally controlled chamber (ESPEC LU-113) keeping the temperature at 25$^{\circ}$.
 Two setups were investigated.
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{center}
@@
 The $\gamma$ source that was used to test the experimental setup was choosen to be an $^{241}Am$.
-The reason for this is that the peak of energy spectrum of the $\gamma$ photons from GRBs is at 50 keV which is very close to the peak of the $^{241}Am$ that is 59.5 keV.
+The reason for this is that the peak of the energy spectrum of the $\gamma$ photons from GRBs is at 50 keV which is very close to the peak of the $^{241}Am$ that is 59.5 keV.
 The activity of the source at the time of the experiment was 471 kBq.
@@
 As the position of the scintillators is not decided yet it is important to understand which configuration would be the best in order to detect as many GRBs as possible.
-Therefore it is vital to understand how the material of the satellite itself absorbs $\gamma$-rays.
+Therefore it is vital to understand how the material of the satellite itself absorbs and scatters $\gamma$-rays.
 The satellite consists of several modules with specific shapes and material contents.
@@
 Therefore an avarage material composition was calculated for all the modules.
-In table $\ref{table:materials}$ the material composition of the 7 modules are listed.
-These materials, mostly alloys consist of several elements.
+In table $\ref{table:materials}$ the material compositions of the 7 modules are listed.
+These materials, mostly alloys, consist of several elements.
 The Geant4 cross section database is built up only for elements.
@@
 100 $\gamma$ particles were used to shoot the satellite with a beam parallel to the plane of the scintillator.
-A scattered $\gamma$ particle can be seen scattered into the scintillator and being detected.
+A $\gamma$-ray can be seen scattered into the scintillator and being detected.
 
@@
 The measured spectra of the scintillation light created by $\gamma$-rays (fig.
-\ref{fig:spectras_meas}) has a main peak that corresponds to the 60 keV $\gamma$s from the $^{241}$Am source.
+\ref{fig:spectras_meas}) have a main peak that corresponds to the 60 keV $\gamma$s from the $^{241}$Am source.
 There is an additional peak with an amplitude of roughly 20 \% of the main peak.
-The physical process that is behind this is the X-ray fluoresence.
+The physical process that is behind this is X-ray fluoresence.
 By default this process is not included in Geant4 simulations, thus I had to turn it on.
 A histogram with and without x-ray fluorescence can be seen in fig.
-\ref{fig:fluo}
+\ref{fig:fluo}.
 
@@
 
-A lead sheet was drilled with nine holes to collimate the $\gamma$ source to certain parts of the scintillator.
+A lead sheet was drilled with nine holes to collimate the $\gamma$-rays to certain parts of the scintillator.
 These measurements were carried out by Kento Torigoe at the University of Hiroshima.
@@
 \includegraphics[width=130.0mm]{images/gammashittingsat.png}
-\caption{The number of detections from the 10,000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
+\caption{The number of detections from the 10,000 $\gamma$ photons in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
 \label{fig:diffpos}
@@
 In fig.
-$\ref{fig:mac17hits}$ one can see the comparison between the energy spectrum measured when the $\gamma$s hit the scintillator with a perpendicular direction and when they hit the satellite from behind.
+$\ref{fig:mac17hits}$ one can see the comparison between the energy spectrum measured when the $\gamma$s hit the scintillator in a perpendicular direction and when they hit the satellite from the side opposite to the scintillator.
 The difference between these two scenarious is that $\gamma$s had to travel through the material of the satellite in the second case.
-About 60 \% of gammas are lost do the absorption of the satellite.
+About 60 \% of gammas are lost due to the absorption in the satellite.
 
@@
 
-A Geant4 Monte-Carlo based simulation was developed in order to understand how the CAMELOT CubeSat would detect $\gamma$-rays originating from short GRBs.
+A Geant4 Monte-Carlo based simulation was developed in order to understand how the CAMELOT CubeSat constallation would detect $\gamma$-rays originating from short GRBs.
 The effect of solar and cosmic electrons on the satellite was also investigated with the simulation.
 
-As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the particle detector of the satellite -- was implemented in Geant4.
+As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the $\gamma$-ray detector of the satellite -- was implemented in Geant4.
 The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs in the simulation with experimental data.
-After the calibration, the results of the simulation was capable of predicting the signal that would be measured in space.
+After the calibration, the results of the simulation are capable of predicting the signal that would be measured in space.
 
 Secondly, the complex CAD model of the satellite --consisting of 7 modules, each with a given avarage material composition-- was exported to Geant4.
-The scintillator and its read out was placed on the side of the satellite.
-
-Thirdly, the $\gamma$ absorption of the satellite was invastigated.
-Parallel $\gamma$-rays with the energy distribution of GRB 9900123 (fig.
-\ref{fig:grb_band}) was simulated.
+The scintillator and its MPPC was placed on the side of the satellite.
+
+Thirdly, the $\gamma$-ray absorption of the satellite was invastigated.
+Parallel $\gamma$-rays with the energy distribution of the bright GRB 9900123 (fig.
+\ref{fig:grb_band}) were simulated.
 36 positions were investigated by varying the incident angle of the $\gamma$s around the major axis of the satellite.
 
-Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at an altitude of 500km.
+Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at an altitude of 500km in a polar orbit.
+It is possible that an other orbit will be choosen for the satellite, as the polar parts of the polar orbit have a very high electron flux.
+
 The satellite was radiated by these particles in Geant4 in the same way that were used for the $\gamma$-rays of GRB 9900123.
